### 2024-11-12 paper/paper.qmd
Add paper introduction

---
title: "gij bent 2"
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
  - name: Julie Nijs
    email: julie.nijs@kuleuven.be
    orcid: 000-0002-7421-9887
    affiliations:
      - name: KU Leuven
format:
  html:
    toc: true
  docx:
    toc: false
editor: source
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
df-print: kable
abstract: |
  TODO
execute:
  echo: false
---

```{r initialisation}
#| output: false
library(scales)

formatn <- function(number) {
    format(round(as.numeric(number), 1), nsmall=0, big.mark=",")
}

formatd <- function(number, nsmall=2) {
    format(round(number, nsmall), nsmall=nsmall)
}

formatp <- function(number) {
    label_percent()(number)
}

suppress_gloss <- FALSE
```

## Introduction {#sec:introduction}

One of the key ideas from usage-based linguistics is that language is not a system that exists just "by itself". Rather, it is widely accepted within this branch that language arises out of the many interactions that language users have with each other [TODO source]. As such, language becomes a "complex-adaptive system" [TODO source], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users. While each speaker of a language (be it Dutch, English or Maori) has their own personalised representation of the rules and constraints that they think make up that language, these representations have enough in common in order to warrant talking about a shared "code", or more broadly, a language.

When it comes to research of said shared code, things become more complicated. It is impossible for researchers to know the complete code of *all* language users in a language system. This situation forces models of language into necessary generalisations. Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian A-curve [as suggested by Kretzschmar, TODO]. The make-up of this curve, with the most popular forms capturing most of the language use anyway, make it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users. Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds. We see this, for example, in probabilistic grammar, [todo definition]. Still, on a theoretical level, it is regrettable that models of variation do not start from the lowest common denominator of this variation: the language user.

[^lects]: i.e. "lects", TODO Geeraerts

Contrastively, the advent of social media offers a unique opportunity for variationist research. Social media platforms offer an insight into the language systems of a large number of people.  Whereas previously it was possible to gauge the linguistic profile of only a small group of people [e.g. Milroy, Labov], social media offer linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [TODO source]. In addition, social media data of course do not provide access to *all* of language for *all* users of a language system; not all utterances are made on social media, nor are all language users active on social media platforms. Nevertheless, social media platforms bring us closer to the idea of studying language *inside out*, starting from individual language users' variation, even if it is only for a single alternation among a subset of language users. This brings us to the first research question of this study:

1. What affordances does a focus on individual variation bring us in the context of alternation research, especially in contrast to traditional, aggregated alternation research?

[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from XXX to XXX. The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.

Another aspect of of the complex-adaptive system of language are the connections between people. Humans are embedded in larger social networks, which are formed according to a so-called "power law". [uitleg scale-free netwerk]
Linguistically, the effects of networks has been studied before [stuk Julie].

- leaders / loaners
- gedrag van centrale figuren
- alle andere dingen die interessant zouden kunenn zijn

Except for small-scale studies [e.g. Milroy & Labov TODO], it has been impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language. Again, social media offer an opportunity here. While it is not practical to get a full network of *all* social media users, we *can* get information on how "connected" a particular user is. Through metrics like "followers" and "following", we know how many connections social media users have. This allows us to get an idea of the centrality of a user in the larger social media network, even if we do not know the full network itself. This brings us to the second research question in this study:

2. How can we leverage the implicit network inherent in social media data to learn more about the spread of linguistic innovations?

To answer the two research questions stated above, we follow up on a study by Sevenants [TODO] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD). To compute the individual variation of different language users, we will use elastic net regression, a regression analysis technique pioneered in [todo]. First, we will introduce the *gij bent* CBD linguistic innovation. Then, we will describe how we modelled the linguistic profiles of the individual user with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study. Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.

### 2024-11-12 paper/paper.qmd
Add section on evolution from diglossia to diaglossia

@@
 Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.
+
+## The case of *gij bent*
+
+This study focusses on *gij bent*, an innovation within Colloquial Belgian Dutch (CBD).
+Before we explain what this innovation is about, we will first explain the general language situation of Dutch in Belgium.
+
+### Dutch in Belgium
+
+Dutch as it is spoken in Belgium has evolved strongly since the second half of the 20^th century.
+Until deep in the 20^th century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [Auer 2005 TODO].
+This means that the Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
+These two were the language modes available to speakers of Dutch.
+From the XXXies TODO onwards, a large-scale language policy campaign attempted to teach those speakers who mastered only their local dialect the standard language.
+While these efforts were well intended, the imposition of a "foreign" standard language -- the standard was imported from the Netherlands -- were met with limited enthusiasm by language users in Flanders.
+However, this language campaign was not without effect, albeit not the intended one.
+
+At the start of the 21^st century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [again Auer 2005].
+In between the dialects and standard language, new language types had appeared, among which so-called "regiolects" (above the dialects) and "regional standards" (below standard language).
+More generally, however, a new term was coined: *tussentaal*, which roughly translates to "interlanguage".
+In this article, we will use the term defined by TODO, "Colloquial Belgian Dutch" or CBD.
+
+The new variant CBD is characterised by being hard to define.
+In general, it is best described as a "standard-adjacent", colloquial form of Belgian Standard Dutch, with both general Flemish elements and region-specific features added to it on all levels (phonology, morphology, syntax etc.).
+The presence of region-specific features means that CBD is not a monolithic language variety, but rather sounds different across all places in Flanders.
+This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [todo citaties Zenner].

### 2024-11-12 paper/paper.qmd
Add a section on 'gij bent'

@@
 This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [todo citaties Zenner].
+
+### *gij bent*
+
+Traditionally in Flanders, if one wishes to say "you are" in an informal way, they would say *gij zijt*.
+*Gij* marks the informal second person pronoun that is typical to most Flemish dialects.
+*Zijt* is a historic form of *zijn* 'to be' that is now exclusively used with this pronoun.
+If one wanted to say "you are" in a formal way (i.e.
+in standard language), they would say *jij bent*.
+*Jij* marks the non-polite, yet formal second person pronoun in Flanders.
+*Jij* is more formal than *gij* because the *jij* pronoun is actually a Netherlandic form that, because it is foreign, has a different status than *gij*.
+*Bent* is the conjugated form that goes along with *jij*.
+It is also imported from the Netherlands.
+
+It is clear, then, that these two forms are distinctly different from each other.
+However, in CBD, a blend of these two forms has appeared: *gij bent*.
+It combines the *gij* pronoun from *gij zijt* with the *bent* conjugation known from standard language.
+*Gij bent* is a quite literal example of the diaglossia situation, as it combines *gij* and *bent* from polar opposites of the language spectrum and meets somewhere in the middle.
+
+Research by [mezelf lol TODO] has shown that *gij bent* most likely originated in dialects from the northern Antwerp province in Flanders, and then spread to other parts of the Brabantian dialect area.[^brabants] The reason for the spread from this area is argued to lie in the function of *gij bent*.
+The *jij bent* from standard language might feel too formal, while the *gij zijt* from dialects might feel too blunt.
+*Gij bent* strikes a balance between the two: it has colloquial roots through Flemish *gij*, but benefits from the prestige associated with standard language [todo referentie] through standard *bent*.
+In addition, both regional, formality and gender effects were found:
+
+1. the use of *gij bent* is limited to the Brabant dialect region only
+2. the use of *gij bent* is less likely in more informal contexts
+3. the use of *gij bent* is more likely for women
+
+[^brabants]: Brabants is the dialect area coinciding, mostly, with the Flemish provinces "Vlaams-Brabant" and "Antwerp".
+It is said to be the driving force behind CBD, but this claim is disputed [todo Lybaert reference].
+
+While these conclusions are drawn from language use originating from social media, the analysis itself is very traditional.
+As in a standard corpus linguistic study, it generalises over all language at once, as well as all language users.
+This leads to blanket statements as the ones above.
+As argued before, there is nothing inherently wrong with this approach, but given the opportunities in social media data, a more bottom-up approach would be interesting.
+More specifically, such an approach would allow us to detect whether certain language users behave differently from what we would expect given their location or gender.
+These deviations from general expectations are now invisible in the generalising models.
+In addition, no account was taken of the network structure hidden in the data, which might reveal more about the forces and the direction this innovation will take in the future.
+
+### Elastic net regression

### 2024-11-13 paper/paper.qmd
Change wording of research question
Fix sup elements

@@
 
-2. How can we leverage the implicit network inherent in social media data to learn more about the spread of linguistic innovations?
+2. How can we leverage the network implicit in social media data to learn more about the spread of linguistic innovations?
 
@@
 
-Dutch as it is spoken in Belgium has evolved strongly since the second half of the 20^th century.
-Until deep in the 20^th century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [Auer 2005 TODO].
+Dutch as it is spoken in Belgium has evolved strongly since the second half of the 20^th^ century.
+Until deep in the 20^th^ century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [Auer 2005 TODO].
 This means that the Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
@@
 
-At the start of the 21^st century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [again Auer 2005].
+At the start of the 21^st^ century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [again Auer 2005].
 In between the dialects and standard language, new language types had appeared, among which so-called "regiolects" (above the dialects) and "regional standards" (below standard language).

### 2024-11-14 paper/paper.qmd
Add methodology section

@@
 
+## Data and methodology
+
+### Dataset
+
+As this study is a follow-up on the *gij bent* study by [mezelf TODO], we will re-use the dataset used in that study.
+The dataset contains [TODO infix] social media posts from Belgium on the Twitter platform (now X).
+These tweets either contain the traditional *gij zijt* or the innovative *gij bent* construction.
+The tweets are tagged for the Flemish dialect region to which each tweet author belongs.
+In addition, gender information was estimated for each tweet author using [todo].
+The dataset also contains a formality distinction for each tweet ("more formal", "more informal"), based on whether a tweet interacts with other people.
+If it does, the idea is that the tweet is conversation-like and thus more informal.
+Each tweet also has a unique (anonymised) identifier, so tweets can be grouped by author.
+This will prove especially useful for this study on individual variation, since we need several tweets in order to gauge the language use of a specific speaker.
+For each author, we also know many accounts they follow, and how many accounts they are followed by.
+This is a metric that is useful for our questions about network influences.
+For our analysis of individual variation, we retained only those authors who have at least 10 tweets in our dataset.
+We did this in order to guarantee a stable estimation of each speaker's language use.
+This operation left us with TODO tweets by TODO unique authors.
+
 ### Elastic net regression
+
+To estimate the individual variation among our tweet authors, we would ideally have a quantitative measure which indicates the deviation of each user from the expected linguistic behaviour.
+Authors who do not deviate would be assigned a (near-)zero value, while those who *do* deviate would receive either a positive or negative value, depending on whether they exceed the expectations for their profiles, or actually go against it.
+In this way, our measure of individual variation truly expresses the peculiarities of each individual speaker.
+
+In order to operationalise this computation of individual variation, we made use of elastic net regression [todo].
+Elastic net regression is an extension of more "traditional" regression techniques [see 2015 Gries, todo].
+Its main innovation is that it uses an extra "penalty" term, which prevents model coefficients, the values associated with model predictors, from growing too large.
+One could think of this as making the model *worse*, but on purpose.
+In practice, this model penalty is applied for two reasons.
+First, it attempts to prevent overfitting.
+Too few data points can skew the estimation of a coefficient, so the penalty is a means to attenuate predictions in such cases.
+Second, the model penalty can function as a way to do variable selection.
+With elastic net, a coefficient can be "punished" to the extent that it nears or equals to zero.
+With this, the predictor of that coefficient is disabled outright.
+We can use this behaviour to enter many predictors in the same analysis at once, and let the model decide which ones are actually interesting.
+
+In addition, elastic net leverages "k-fold cross validation".
+This technique divides the data into several parts and iteratively uses different parts for training and testing the regression model.
+This practice also contributes towards general robustness and the prevention of overfitting.
+K-fold cross validation allows us to have hundreds of predictors in a single analysis, which is a useful property when we want to track a multitude of language users at the same time.
+Such a thing would be impossible with a regular regression analysis on the basis of mathematical intractability (i.e.
+with mixed models).
+
+In general, then, elastic net regression lends itself nicely to research into individual variation.
+With elastic net, we estimated coefficients for each language user separately by treating those language users as individual predictors.
+Because we also included all the predictors from [sevenants todo] in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
+Due to the multifactorial control characteristic[^multifactoriality] of regression analysis, this makes it so each individual speaker's coefficient becomes a measure of the variation that is not explained on the basis of the more general predictor terms, i.e.
+the individual deviation or variation we expressed our desire for in the previous sections.
+
+[^multifactoriality]: Multifactorial control means that the analysis takes all predictors into account at the same time.
+This guarantees that variation due to one predictor is not assumed to stem from another.
+
+For an overview of all predictors included in our model, see @tbl-predictors.
+
+|predictor|explanation|
+|---|---|
+|dialect\*|the dialect area the tweet poster belongs to ("West Flemish", "East Flemish", "Brabantian", "Limburgish")
+|gender|the estimated gender of the tweet poster -- generated automatically|
+|distance from northern Antwerp|the distance of the poster's location in km from the northern Antwerp area|
+|formality|the formality of the tweet -- derived from whether the tweet author interacts with another user in the tweet|
+|user_id\*|a unique (anonymised) identifier for the tweet author -- allows us to know which tweets belong to the same person|
+
+: An overview of all predictors which will be used in the elastic net regression.
+Predictors marked with \* receive separate predictors for each level (for example, separate predictors for each tweet author).
+{#tbl-predictors}

### 2024-11-15 paper/paper.qmd
Some minor corrections
Add notice about ElasticToolsR
Add control variables analysis

@@
 suppress_gloss <- FALSE
+```
+
+```{r load-coefficients}
+#| output: false
+
+# Load the dataset
+source("../analysis/0-common.R")
+
+coefficients_full <- read.csv("../output/gij_bent_coefficients_two_genders.csv")
+
+coefficients <- merge(x = coefficients_full %>% subset(substr(feature, 1, 1) != "_"),
+               y = df %>% one_user_one_tweet,
+               by.x = "feature",
+               by.y = "user_id",
+               all.x = TRUE)
+coefficients$log_followers = log(coefficients$user_followers_count)
+coefficients$log_following = log(coefficients$user_friends_count)
+coefficients$log_tweet_count = log(coefficients$user_tweet_count)
+coefficients$influence = log((coefficients$user_followers_count + 0.001) / (coefficients$user_friends_count + 0.001))
+
 ```
@@
 Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.
+TODO nakijken of dit nog klopt
 
@@
 with mixed models).
+For additional details on elastic net regression for linguistics, see [mezelf geaccepteerd leuk].
 
 In general, then, elastic net regression lends itself nicely to research into individual variation.
-With elastic net, we estimated coefficients for each language user separately by treating those language users as individual predictors.
+With elastic net, we modelled the presence of either *zijt* (conservative) or *bent* (innovative) as a logistic response variable.
+In our model, we estimated coefficients for each language user separately by treating those language users as individual predictors.
 Because we also included all the predictors from [sevenants todo] in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
@@
 {#tbl-predictors}
+
+For our analysis, we used ElasticToolsR [todo mezelf], a package for the R language [todo] which simplifies running elastic net regression models.
+
+## Results
+
+In this section, we will go over the results produced by our elastic net regression model.
+We will  first look at the predictors included in the previous study to ensure our model produces comparable results.
+Then, we will dive into the predictors describing the behaviour of the individual language users.
+
+### Controlling predictors
+
+@tbl-other-coefficients gives an overview of the "control" coefficients that were included in order to have multifactorial control for the individual variation.
+Since the innovative *bent* variant was encoded as outcome "1", and the innovative *zijt* was encoded as outcome "0", positive coefficients mean a a correction towards the innovative variant, while negative corrections mean a correction towards the conservative variant.
+These corrections must be interpreted from the situation expressed in the intercept, a "reference situation" that is defined as follows:
+
+- formal situation (no reply or interaction)
+- at distance "0" from northern Antwerp
+
+In general, the results are comparable to those from [mezelf].
+The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections).
+We even see the same anomaly for the West-Flemish dialect area[^anomaly].
+*gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo).
+Compared to [mezelf todo], some predictors have more subtle effects.
+We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- [mezelf todo] used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in [mezelf todo] will now be attributed to individual variation.
+
+[^anomaly]: The results for the West-Flemish dialect area need to be interpreted in conjunction with the "distance from northern Antwerp" parameter.
+The regression analysis assumes a zero distance from Antwerp from the intercept, but this does not make sense for dialect areas other than Brabant.
+Therefore, if we apply the extra corrections expressed in "distance from northern Antwerp", we get the expected negative correction towards the conservative form (`r 121 * -0.017`).
+Still, the *gij* pronoun is quite rare in this area, so the West-Flemish results should be treated with caution.
+
+```{r #tbl-other-coefficients}
+# All other coefficients start with an underscore
+other_coefficients <- coefficients_full[coefficients_full$feature %>% substr(1,1) == "_",]
+# Change "removed" to "retained"
+other_coefficients$retained = ifelse(other_coefficients$coefficient == 0, "no", "yes")
+# Friendly names
+other_coefficients$feature <- gsub("_(.+)", "\\1", other_coefficients$feature)
+other_coefficients$feature <- gsub("(is|_)", " ", other_coefficients$feature)
+other_coefficients$predictor <- other_coefficients$feature
+other_coefficients$coefficient <- other_coefficients$coefficient %>% formatd(3)
+# Only keep interesting columns
+other_coefficients <- other_coefficients[, names(other_coefficients) %in% c("coefficient", "predictor", "retained")]
+# Re-order
+other_coefficients <- other_coefficients[,c(3, 1, 2)]
+# Sort
+other_coefficients$coefficient <- as.numeric(other_coefficients$coefficient)
+other_coefficients <- other_coefficients[order(other_coefficients$coefficient,
+                                               decreasing=TRUE),]
+# Remove row indices
+rownames(other_coefficients) <- NULL
+# Output to document
+other_coefficients
+```

### 2024-11-15 analysis/1-elastic-net.R
Throw away unknown gender records to retain parity

@@ -12,7 +12,7 @@ source("0-common.R")
 
 
 # Create an ElasticTools dataset
-ds <- dataset(df=df,
+ds <- dataset(df=df %>% no_unknown_gender(),
               response_variable_column="construction_type",
               to_binary_columns=c("user_id", "dialect", "gender"),
               other_columns=c("distance_from_antwerp", "is_reply"))

### 2024-11-20 paper/paper.qmd
Explain removal of non-gendered tweets
Add remaining results sections (skeleton)
Add note for Julie

@@
 
+[ @ Julie: misschien hier een stuk over het reeds bestaande onderzoek naar individuele variatie. hoeft niet veel te zijn maar nu staat er niets en dat is misschien niet top ]
+
 Another aspect of of the complex-adaptive system of language are the connections between people.
@@
 In addition, gender information was estimated for each tweet author using [todo].
+Authors for whom gender could not be established were removed, to retain parity with [mezelf TODO].
 The dataset also contains a formality distinction for each tweet ("more formal", "more informal"), based on whether a tweet interacts with other people.
@@
 We did this in order to guarantee a stable estimation of each speaker's language use.
-This operation left us with TODO tweets by TODO unique authors.
+After all filtering operations, we were left with TODO tweets by TODO unique authors.
 
@@
 ```
+
+### Individual variation
+
+[density plot]
+
+[violin plots]
+
+[profiles: most extreme corrections per author]
+
+[regression analysis]
+
+[network effect explanation]
+
+## Conclusion

### 2024-11-20 paper/paper.qmd
Move footnote

@@
 The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections).
-We even see the same anomaly for the West-Flemish dialect area[^anomaly].
-*gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo).
+We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo).
 Compared to [mezelf todo], some predictors have more subtle effects.

### 2024-11-20 analysis/2-analysis-gam.R
Add GAM code

@@ -1,0 +1,220 @@
+library(mgcv) # GAM
+library(sf) # geographic data
+library(tidyr) # expand_grid
+library(ggthemes) # for map theme
+library(cowplot) # plot_grid
+library(dplyr) # group_by
+library(scales) # percent
+library(nngeo) # removing the Brussels hole
+
+source("0-common.R")
+
+df_solo <- coefficients
+
+#
+# GAM
+#
+
+build_gam <- function(df) {
+  fit <- gam(
+    coefficient ~ s(long) + s(lat) + te(long, lat),
+    data = df,
+    family = gaussian,
+    method = "REML"
+  )
+  
+  return(fit)
+}
+
+# Shapefiles
+
+# == Flanders and Wallonia ==
+flanders <- st_read(dsn = "maps/regions/régions_08.shp")
+brussels <- flanders[flanders$Nom == "Bruxelles-Capitale",] # Bonjour
+flanders <-
+  flanders[flanders$Nom == "Vlaams Gewest", ] # Wallonia bye
+flanders <- st_transform(flanders, 4326) # convert to GPS coordinates system
+brussels <- st_transform(brussels, 4326)
+
+# == Noorderkempen area ==
+noorderkempen <- st_read("maps/Noorderkempen/POLYGON.shp")
+noorderkempen <- st_transform(noorderkempen, 4326)
+
+noorderkempen <- st_intersection(flanders, noorderkempen)
+
+# == Dialect area borders ==
+dialects <- st_read("maps/dialects/POLYGON.shp")
+dialects <- st_transform(dialects, 4326)
+
+# == Municipalities ==
+gemeenten <- st_read("maps/gemeenten/Refgem.shp")
+gemeenten <- st_transform(gemeenten, 4326)
+# Remove superfluous data
+keep_columns <- c("NAAM", "geometry")
+gemeenten <- subset(gemeenten, select = keep_columns)
+# Prepare Brussels for a merger
+# (lol, this is not a political statement I promise)
+brussels$NAAM <- c("Brussel")
+brussels <- subset(brussels, select = keep_columns)
+# Merger! Don't tell the Flemish nationalists
+gemeenten <- rbind(gemeenten, brussels)
+
+# Read the postal codes dataset
+df_zip <- read.csv("../data/zipcode-belgium.csv",
+                   header=FALSE,
+                   col.names = c("zip", "name", "long", "lat"))
+df_zip$key = tolower(df_zip$name)
+
[…]

### 2024-11-20 paper/paper.qmd
Add individual variation pattern code

@@
 library(scales)
+library(ggplot2)
 
@@
 
-### Controlling predictors
+### Controlling predictors {#sec-controlling-predictors}
 
@@
 
-[density plot]
+In this section, we will go over the coefficients that were computed for each language user.
+We will first look at the variation patterns globally, and then zoom in on the differences between different groups of language users.
+We will also attempt to model the coefficients in order to find relations between them.
+
+#### Global variation pattern
+
+First, we will look at the coefficient globally.
+The density plot of the variation coefficients in @fig-general-density gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc..
+Negative coefficients on the left side of the plot show deviations of individual language users towards the conservative *gij zijt*.
+Positive coefficients on the right side of the plot show deviations of individual language users towards the innovative *gij bent*.
+The middle dotted line marks the zero coefficient, i.e.
+those who do not deviate from the expected norm.
+We see that there is a bi-modal distribution in the variation coefficients.
+The first distribution shows many slights corrections towards the conservative form (first bump).
+The second distribution shows a smaller number of larger corrections towards the innovative form (second bump).
+This bi-modal variation pattern would have remained invisible in a more traditional regression model.
+
+Note that each of the two different distributions might not consist of a homogeneous type of people.
+For example, the innovative corrections might include people in regions where the innovative form is rarely used, and who use the innovative form nonetheless.
+At the same time, innovative corrections might also stem from people in an already innovative area who "out-innovate" the expectations, using the innovative form even more often than is expected.
+We will attempt to build profiles of each correction direction later TODO.
+
+```{r #fig-general-density}
+#| fig-cap: A density plot describing the individual variation coefficients in our dataset.
+The left side of the plot (negative coefficients) shows corrections towards the conservative form, the right side of the plot (positive coefficients) shows corrections towards the innovative form.
+coefficients %>%
+  ggplot(aes(x = coefficient)) +
+  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.5) +
+  geom_vline(xintercept=0, color="black", linewidth=1, linetype="dotdash")
+```
+
+#### Variation patterns among groups
+
+Next, we will look at the patterns of variation among different groups.
+@fig-gender-violin shows the distribution of variation coefficients between men and women.
+Interestingly, we see patterns that "reverse" the known patterns from [mezelf todo] and @sec-controlling-predictors: men correct towards the innovative variant, women correct towards the conservative variant.
+This makes sense: of course, though there are general trends that dictate a certain preference for men or women, this does not mean that *all* individuals from that group follow that same pattern.
+This is what we see in our plots of individual variation.
+There are ample outliers who deviate from what is typically expected from their gender, and this also highlights that we need to be cautious when making generalisations in this regard.
+
+```{r #fig-gender-violin}
+#| fig-cap: A violin plot describing the individual variation coefficients for men and women. A wider figure means more data for that y value.
+coefficients %>%
+  ggplot(aes(x = gender, y = coefficient, fill = gender)) +
+  geom_violin() +
+  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
+```
+
+@fig-region-violin shows the dispersion of variation by Flemish dialect region.
+Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.
+The Brabant dialect shows individual variation which is comparable both for innovative and conservative variants, whereas the other dialects gravitate towards more conservative corrections.
+We see that there are innovators in all three non-Brabant regions, but they are generally few.
+Maybe these are near border-regions?
+TODO
+
+```{r #fig-region-violin}
+#| fig-cap: A violin plot describing the individual variation coefficients by region. A wider figure means more data for that y value.
+coefficients %>%
+  ggplot(aes(x = dialect, y = coefficient, fill = dialect)) +
+  geom_violin() +
+  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
+```
+
+Just from this general overview, we see that there are patterns among the variation.
+Though speakers are of course free to use whatever forms they want, how they deviate from expectations is not random.
 
 [violin plots]
+
+### Profile analysis
 

### 2024-11-20 paper/paper.qmd
Discuss GAM results

@@
 Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.
-The Brabant dialect shows individual variation which is comparable both for innovative and conservative variants, whereas the other dialects gravitate towards more conservative corrections.
-We see that there are innovators in all three non-Brabant regions, but they are generally few.
-Maybe these are near border-regions?
-TODO
+There seem to be two variation profiles: a Brabant and a non-Brabant variation profile.
+The Brabant dialect shows individual variation which is comparable both for innovative and conservative variants.
+In the three non-Brabant regions, we see that there are some innovators, but they are generally few -- the dialects gravitate towards more conservative corrections.
 
@@
 
-Just from this general overview, we see that there are patterns among the variation.
+One might wonder whether the few innovators that do appear in the plots are perhaps those that live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
+To study this, we built a Generalised Additive Model or GAM [todo ref].
+A GAM can fit smooth curves to "wavy" data.
+If extrapolated to two dimensions, it allows one to create "weatherman-like" heatmaps for linguistic data.
+In this case, we modelled the elastic net coefficients on the basis of the latitude and longitude values associated with the places in the profiles of the Twitter users, according to the following equation:
+
+todo equation
+
+We will immediately shift towards the visual interpretation of the GAM in TODO.
+Dark blue colours show corrections towards the conservative variant, whereas light yellow colours show corrections towards the innovative variant.
+Beware to keep in mind, however, that these corrections are to be interpreted against the expected behaviour in that specific dialect region.
+In the GAM plot, we see that the northern Antwerp region is specifically innovative in contrast to an already innovative dialect region, Brabant.
+This is expected from the results by [mezelf todo].
+What is especially interesting given our interest in the innovators in the non-Brabant regions, is that we indeed see that areas closer to the Brabant border show corrections that tend more towards the innovative variant.
+In addition, we also see that there seems to be an additional horizontal diffusion pattern, where the more innovative variant seems to spread from east to west in the east and from west to east in the west.
+This pattern remained invisible in the original study by [mezelf todo].
+Computer simulations have shown that border-adjacent speakers can play an important role as gatekeepers of innovations, since their hybrid identity can form a "bridge" through which innovations can be passed on [todo OOK mezelf].
+In a sense, the horizontal positive variation coefficient pattern shows the pathway that *gij bent* might take in the future in order to break through in these other dialect regions.
+
+TODO figure
+
+In general, then, we see that there are two trends in the variation coefficients.
+Firstly, for gender, we see a "reversal" pattern, where typical behaviour is not shared across the entire gender group.
+Secondly, we see a wave-like [todo wave linguistics] horizontal diffusion pattern in the non-Brabant dialect regions, even in regions which, in the general analysis, are thought to be rather conservative.
 Though speakers are of course free to use whatever forms they want, how they deviate from expectations is not random.

### 2024-11-26 paper/paper.qmd
Fix: 'innovative' > 'conservative'

@@
 @tbl-other-coefficients gives an overview of the "control" coefficients that were included in order to have multifactorial control for the individual variation.
-Since the innovative *bent* variant was encoded as outcome "1", and the innovative *zijt* was encoded as outcome "0", positive coefficients mean a a correction towards the innovative variant, while negative corrections mean a correction towards the conservative variant.
+Since the innovative *bent* variant was encoded as outcome "1", and the conservative *zijt* was encoded as outcome "0", positive coefficients mean a a correction towards the innovative variant, while negative corrections mean a correction towards the conservative variant.
 These corrections must be interpreted from the situation expressed in the intercept, a "reference situation" that is defined as follows:

### 2024-11-26 paper/paper.qmd
Correct for two-gender solution

@@
 - at distance "0" from northern Antwerp
+- for users assumed to be male
 
@@
 We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo).
-Compared to [mezelf todo], some predictors have more subtle effects.
+We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*.
+Compared to [mezelf todo], some predictors have more subtle effects (todo welke).
 We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- [mezelf todo] used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in [mezelf todo] will now be attributed to individual variation.
@@
 other_coefficients$feature <- gsub("_(.+)", "\\1", other_coefficients$feature)
-other_coefficients$feature <- gsub("(is|_)", " ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(is_|_)", " ", other_coefficients$feature)
 other_coefficients$predictor <- other_coefficients$feature

### 2024-11-26 analysis/0-common.R
Use two-level factor for gender

@@ -25,6 +25,7 @@ df$gender <- factor(df$gender,
 
 # If a user is mentioned in the tweet, we consider it a "reply"
 df$is_reply <- df$mentioned_users_count > 0
+df$is_reply <- ifelse(df$is_reply, "reply", "no_reply")
 # Has to be turned into a factor to work in some plots
 df$is_reply <- as.factor(df$is_reply)
 
@@ -48,5 +49,9 @@ one_user_one_tweet <- function(df) {
 }
 
 no_unknown_gender <- function(df) {
-  subset(df, gender != "_is_gender_unknown")
+  df <- subset(df, gender != "_is_gender_unknown")
+  df$gender <- ifelse(df$gender == "_is_gender_male", "male", "female")
+  df$gender <- factor(df$gender, levels = c("male", "female"))
+  return(df)
 }
+

### 2024-11-26 analysis/1-elastic-net.R
Use two-level gender system in the larger analysis

@@ -10,12 +10,11 @@ source("ElasticToolsR/MetaFile.R")
 # Load the dataset
 source("0-common.R")
 
-
 # Create an ElasticTools dataset
 ds <- dataset(df=df %>% no_unknown_gender(),
               response_variable_column="construction_type",
-              to_binary_columns=c("user_id", "dialect", "gender"),
-              other_columns=c("distance_from_antwerp", "is_reply"))
+              to_binary_columns=c("user_id", "dialect"),
+              other_columns=c("distance_from_antwerp", "is_reply", "gender"))
 
 # Get the list of features
 # In our case, this is the list of users
@@ -38,7 +37,7 @@ coefficients_with_labels <- net$attach_coefficients(
   output$fits[[lowest_loss_row[["X_id"]]]])
 
 # Export
-write.csv(coefficients_with_labels, "../output/gij_bent_coefficients.csv",
+write.csv(coefficients_with_labels, "../output/gij_bent_coefficients_two_genders.csv",
           row.names=FALSE)
 
 #

### 2024-11-26 analysis/2-analysis.R
Change output name for analysis

@@ -8,7 +8,7 @@ source("0-common.R")
 # Plots
 #
 
-coeff <- read.csv("../output/gij_bent_coefficients.csv")
+coeff <- read.csv("../output/gij_bent_coefficients_two_genders.csv")
 
 coeff <- merge(x = coeff %>% subset(substr(feature, 1, 1) != "_"),
                y = df %>% one_user_one_tweet,

### 2024-11-26 paper/paper.qmd
Better flow from controlling predictors to individual variation

@@
 We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- [mezelf todo] used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in [mezelf todo] will now be attributed to individual variation.
+Still, broadly speaking, the results remain comparable.
+Therefore, we can safely move on to the discussion of the individual variation.
 
@@
 other_coefficients$feature <- gsub("_(.+)", "\\1", other_coefficients$feature)
-other_coefficients$feature <- gsub("(is_|_)", " ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(dialect_)", "dialect: ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(is_)", " ", other_coefficients$feature)
 other_coefficients$predictor <- other_coefficients$feature

### 2024-11-26 paper/paper.qmd
Further clean up regression table

@@
 other_coefficients$feature <- gsub("(dialect_)", "dialect: ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(gender_)", "gender: ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(reply_)", "reply: ", other_coefficients$feature)
 other_coefficients$feature <- gsub("(is_)", " ", other_coefficients$feature)

### 2024-11-26 analysis/0-common.R

@@ -25,7 +25,7 @@ df$gender <- factor(df$gender,
 
 # If a user is mentioned in the tweet, we consider it a "reply"
 df$is_reply <- df$mentioned_users_count > 0
-df$is_reply <- ifelse(df$is_reply, "reply", "no_reply")
+df$is_reply <- ifelse(df$is_reply, "reply_yes", "reply_no")
 # Has to be turned into a factor to work in some plots
 df$is_reply <- as.factor(df$is_reply)
 
@@ -50,8 +50,8 @@ one_user_one_tweet <- function(df) {
 
 no_unknown_gender <- function(df) {
   df <- subset(df, gender != "_is_gender_unknown")
-  df$gender <- ifelse(df$gender == "_is_gender_male", "male", "female")
-  df$gender <- factor(df$gender, levels = c("male", "female"))
+  df$gender <- ifelse(df$gender == "_is_gender_male", "gender_male", "gender_female")
+  df$gender <- factor(df$gender, levels = c("gender_male", "gender_female"))
   return(df)
 }
 

### 2024-11-26 analysis/2-analysis.R
Re-introduce distance from Antwerp parameter

@@ -100,7 +100,7 @@ fanatic_bent_user <- coeff[which.max(coeff$coefficient),]
 # Analysis
 #
 
-fit <- lm(coefficient ~ influence + dialect + gender, data=coeff %>% no_unknown_gender())
+fit <- lm(coefficient ~ influence + dialect + gender + distance_from_antwerp, data=coeff %>% no_unknown_gender())
 summary(fit)
 
 posthoc <- emmeans(fit,

### 2024-11-26 paper/paper.qmd
Improve regression table output once more

--- 2024-11-26 paper/paper.qmd
@@
 other_coefficients$feature <- gsub("(dialect_)", "dialect: ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(gender_)", "gender: ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(reply_)", "reply: ", other_coefficients$feature)
 other_coefficients$feature <- gsub("(is_)", " ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(_)", " ", other_coefficients$feature)
+other_coefficients$feature <- gsub("(antwerp)", "Antwerp (km)", other_coefficients$feature)
 other_coefficients$predictor <- other_coefficients$feature

### 2024-11-27 paper/paper.qmd
Fix congruence mistake: 'make' > 'makes'

@@
 Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian A-curve [as suggested by Kretzschmar, TODO].
-The make-up of this curve, with the most popular forms capturing most of the language use anyway, make it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users.
+The make-up of this curve, with the most popular forms capturing most of the language use anyway, makes it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users.
 Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds.

### 2024-11-27 paper/paper.qmd
Specify: 'control' results
Specify the differences between our results and those of Sevenants

@@
 
-In general, the results are comparable to those from [mezelf].
+In general, the control variable results are comparable to the results from [mezelf].
 The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections).
@@
 We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*.
-Compared to [mezelf todo], some predictors have more subtle effects (todo welke).
+Compared to [mezelf todo], some predictors have more subtle effects.
+Especially the distance correction and the formality distinction correction are smaller.
 We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- [mezelf todo] used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in [mezelf todo] will now be attributed to individual variation.

### 2024-11-27 paper/paper.qmd
Further talk about bimodal distribution found in the coefficients

@@
 At the same time, innovative corrections might also stem from people in an already innovative area who "out-innovate" the expectations, using the innovative form even more often than is expected.
-We will attempt to build profiles of each correction direction later TODO.
+We will attempt to tease out this distinction in the next section.
 
@@
 Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.
-There seem to be two variation profiles: a Brabant and a non-Brabant variation profile.
-The Brabant dialect shows individual variation which is comparable both for innovative and conservative variants.
-In the three non-Brabant regions, we see that there are some innovators, but they are generally few -- the dialects gravitate towards more conservative corrections.
+There seem to be two variation profiles: a Brabant variation profile, and a non-Brabant variation profile.
+The Brabant dialect shows a slight preference for innovation at the upper end of the coefficient values, with declining coefficents towards conserative corrections.
+In the three non-Brabant regions, we see that there are some innovators, but they are generally few.
+In these dialects, the values gravitate towards more conservative corrections.
+With these results, we have an explanation for the bi-modal nature of @fig-general-density: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region.
+The second distribution, centred *above* zero, consists mostly of eager innovators from the already innovative Brabant dialect area.
 

### 2024-11-27 paper/paper.qmd
Further discuss individual variation plots

@@
 
+##### Gender
+
 Next, we will look at the patterns of variation among different groups.
 @fig-gender-violin shows the distribution of variation coefficients between men and women.
-Interestingly, we see patterns that "reverse" the known patterns from [mezelf todo] and @sec-controlling-predictors: men correct towards the innovative variant, women correct towards the conservative variant.
-This makes sense: of course, though there are general trends that dictate a certain preference for men or women, this does not mean that *all* individuals from that group follow that same pattern.
-This is what we see in our plots of individual variation.
-There are ample outliers who deviate from what is typically expected from their gender, and this also highlights that we need to be cautious when making generalisations in this regard.
+There are two key points.
+First, we see that men and women have comparable profiles, with the same bi-modal trend seen in the general coefficients overview.
+We will address this bi-modality in the section on dialect variation patterns.
+
+Secondly, we see that the most extreme innovative corrections in the plot stem from men, while the most extreme conservative corrections stem from women.
+This is peculiar, in the sense that this pattern "reverses" what we know from from [mezelf todo] and @sec-controlling-predictors.
+However, keep in mind that the plot shows *corrections* on top of *expectations*.
+Though there are general trends that dictate a certain preference for men or women, this does not mean that *all* individuals from that group follow that same pattern.
+@fig-gender-violin shows this reversal: there are ample outlier speakers who deviate from what is typically expected from their gender, and this also highlights the need to be cautious when making generalisations in this regard.
 
@@
 
-@fig-region-violin shows the dispersion of variation by Flemish dialect region.
-Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.
+##### Dialect
+
+Next, we look at the dispersion of variation by Flemish dialect region in @fig-region-violin.
+Here, we do not see a "reversal" pattern, in contrast to @fig-gender-violin.
 There seem to be two variation profiles: a Brabant variation profile, and a non-Brabant variation profile.
-The Brabant dialect shows a slight preference for innovation at the upper end of the coefficient values, with declining coefficents towards conserative corrections.
+The Brabant variation profile shows how in the Brabant dialect region, there is  a slight preference for innovation at the upper end of the coefficient values, with declining coefficents towards conserative corrections.
 In the three non-Brabant regions, we see that there are some innovators, but they are generally few.
 In these dialects, the values gravitate towards more conservative corrections.
-With these results, we have an explanation for the bi-modal nature of @fig-general-density: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region.
+With these results, we have an explanation for the bi-modal nature of @fig-general-density: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region, and therefore correct "downwards".
 The second distribution, centred *above* zero, consists mostly of eager innovators from the already innovative Brabant dialect area.
+As avid users of the innovative form, they correct "upwards" in our plots.
 

### 2024-11-27 paper/paper.qmd
Make GAM intro more smooth

@@
 
-One might wonder whether the few innovators that do appear in the plots are perhaps those that live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
-To study this, we built a Generalised Additive Model or GAM [todo ref].
+We see in @fig-region-violin that, while they are few, innovators in non-Brabant dialect areas *do* exist.
+One might wonder what the profile of these rare innovators is.
+Perhaps they they live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
+To answer this question, we built a Generalised Additive Model or GAM [todo ref].
 A GAM can fit smooth curves to "wavy" data.

### 2024-11-28 paper/paper.qmd
Discuss absence of real differences between male and female coefficients
Treat the linear regression results

@@
 library(ggplot2)
+library(broom)
+library(dplyr)
+library(tidycat)
+library(emmeans)
 
@@
 
+```
+
+```{r regression-fit-format}
+format_num_col <- function(p_value) {
+  if (p_value < 0.01) {
+    return("<0.01")
+  } else {
+    return(formatd(p_value, 4))
+  }
+}
+format_num_col <- Vectorize(format_num_col)
+
+format_table <- function(df) {
+  df <- df %>% tidy %>% 
+    tidy_categorical(m = df) %>% 
+    filter(!is.na(term)) %>% 
+    select(-c(reference, term, effect)) %>%
+    mutate(variable = as.character(variable),
+           level = as.character(level)) %>%
+    mutate(level = ifelse(variable == level, "", level),
+           variable = as.character(variable)) %>% 
+    #group_by(variable) %>%
+    #mutate(variable = ifelse(row_number() == 1, variable, "")) %>%
+    #ungroup() %>%
+    mutate(term = ifelse(level != "", paste0(variable, ": ", level), variable)) %>%
+    select(-c(variable, level))
+  df <- df[, c("term", "estimate", "std.error", "statistic", "p.value")]
+
+  df$sig <- ifelse(df$p.value <= 0.05, "*", "")
+
+  df$estimate <- df$estimate %>% formatd(2)
+  df$std.error <- df$std.error %>% formatd(2)
+  df$statistic <- df$statistic %>% formatd(2)
+  df$p.value <- df$p.value %>% format_num_col()
+
+  colnames(df) <- c("term", "coefficient", "std. error", "t value", "p value", " ")
+
+  return(df)
+}
+
+format_posthoc_table <- function(df) {
+  df <- df$contrasts %>% tidy()
+  df$term <- NULL
+  df$df <- NULL
+  df$null <- NULL
+  df$null.value <- NULL
+  df$contrast <- gsub("[()]", "", df$contrast)
+  df$contrast <- gsub("-", "↔", df$contrast)
+
+  df$sig <- ifelse(df$adj.p.value <= 0.05, "*", "")
+
+  df$estimate <- df$estimate %>% formatd()
+  df$std.error <- df$std.error %>% formatd()
+  df$statistic <- df$statistic %>% formatd()
+  df$adj.p.value <- df$adj.p.value %>% format_num_col()
+
+  colnames(df) <- c("contrast", "coefficient", "std. error", "t value", "p value", "")
+
+  return(df)
+}
 ```
@@
 @fig-gender-violin shows this reversal: there are ample outlier speakers who deviate from what is typically expected from their gender, and this also highlights the need to be cautious when making generalisations in this regard.
+At the same time, the distributions between men and women are still similar enough that we likely cannot speak of distinctly different profiles.
+We will come back to this in our regression model of the coefficients in section TODO.
 
@@
 
-### Profile analysis
+#### Network effects
 
-[profiles: most extreme corrections per author]
+As mentioned in INTRODUCTION TODO, the networked aspect of social media data provides an opportunity for researchers to investigate which people use what variant, and what that says about the diffusion of a new variant.
+Since our dataset comes from the Twitter platform, we also dispose of metrics which define a user's relative popularity on the platform.
+The first metric, "Followers", tallies how many other users want to see a user's posts appear in their own social media feed.
+Users with a large number of followers have a broad reach, and therefore have the possibility to be influential in their language use.
+The second metric, "Following", states how many other people's posts a user wants to see in their social media feed.
+Users who follow a large number of other users have the opportunity of being exposed to a larger linguistic pallette -- though this need not necessarily be the case.
 
-[regression analysis]
+To assess the influence of the users in our dataset within the larger Twitter network, we devised a metric which is based on the ratio between "Followers" and "Following".
+The idea of the metric is that users who have a large number of followers, yet follow few people themselves, have a larger relative influence than users without this asymmetry.
+Our influence metric is shown in Equation TODO.
+
+$$
+\log{
+  \frac{
+    \text{\# followers} + 0.001
+  } {
+    \text{\# following} + 0.001
+  }
+}
+$$
+
+Our influence metric is based on the priming ratio from [mezelf geaccepteerd leuk] and hinges on logarithm and Laplace smoothing (TODO).
+The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts.
+Where some users have thousands of followers, some only have a few.
+The use of the logarithm scales this discrepancy down.
+In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users.
+The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`).
+The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e.
+users who have more followers than they themselves follow people.
+This is expected, since [todo parlee over disparity tussen posters en lurkers].
+
+```{r #fig-influence}
+boxplot(coefficients$influence, horizontal = T)
+```
+
+In our case, we want to know how the language users who are thought to be influential in our network behave.
+Are they are the forefront of innovation, or are they conservative?
+Depending on what profile we find, we might be able to discern in what phase of diffusion the *gij bent* innovation is situated (see Section TODO).
+
+To answer this question, we built a common linear regression model.
+We model the coefficients in term of the influence of the users, but we also supplement our analysis with the dialect and gender distinctions we discussed earlier.
+Bundling all these possible influences in the same model will ensure that we do not accidentally assign variation between language users to the wrong source.
+It will also function as an extra check for the results from Section TODO, as we will now be able to check statistically whether the distinctions we spotted in the visual exploration are statistically significant distinctions.
+@tbl-linear-predictors gives an overview of the predictors that were used in the linear regression model.
+
+|predictor|explanation|
+|---|---|
+|dialect|the dialect area the tweet poster belongs to ("West Flemish", "East Flemish", "Brabantian", "Limburgish")
+|gender|the estimated gender of the tweet poster -- generated automatically|
+|influence|a metric expressing the relative influence of a language user within the Twitter network|
+
+: An overview of all predictors used in the linear regression model. {#tbl-linear-predictors}
+
+```{r linear-regression-model}
+fit <- lm(coefficient ~ gender + dialect + influence, data=coefficients %>% no_unknown_gender())
+fit %>% format_table()
+```
+
+We will first go over the controlling variables we discussed earlier, and then move on to the influence predictor.
+
+1. Intercept
+
+First, we look at the intercept of the model.
+Just like in TODO, the intercept here expressed the "default" situation against which further corrections need to be understood.
+Here, the intercept expresses a language user ...
+
+- ... from the Brabant dialect area
+- ... who is assumed to be male
+- ... with an influence of "zero"
+
+Our intercept starts from a value of TODO, which shows a slight bias for innovative behaviour. All further corrections need to be understood relative to this value.
+
+2. Gender
+
+We see that the distinction between users who are thought to be male and users who are thought to be female does not reach the significance threshold.
+Therefore, the differences which we discussed in TODO are not different enough to the degree that they are actually distinct.
+Still, the fact that the *tendency* is clearly there is still interesting, and the reversal of the extreme values of course still holds.
+
+3. Dialect area
+
+Next, we also see that there are significant differences between the reference dialect area (Brabant) and all other dialect areas.
+As was already clear from the visual inspection of the corrections per dialect area, we see that in non-Brabant areas, the corrections tend towards the conservative form, whereas Brabant area corrections are mostly innovative.
+
+In addition, we wanted to know whether there are also differences *between* the non-Brabant dialact areas.
+To investigate this, we ran a post-hoc analysis through emmeans (TODO).
+In this post-hoc analysis, we check for each dialect area pair whether there are significant differences in individual variation between the two.
+We see in @tbl-posthoc-test that there are *no* further differences between the non-Brabant dialect areas.
+Our assessment of the two variation profiles was thus correct.
+
+```{r #tbl-posthoc-test}
+posthoc <- emmeans(fit,
+                   pairwise ~ dialect,
+                   type="response",
+                   weights="proportional")
+
+posthoc %>% format_posthoc_table()
+```
+
+4. Network influence
 

### 2024-11-28 paper/paper.qmd
Describe network influence results

@@
 
+Finally, we look at the network influence parameter.
+Recall that our influence predictor expresses the (im)balance between the "followers" and "following" metrics, with those users who are followed by more people than they follow themselves being attributed a larger influence.
+The regression table in @tbl-linear-predictors shows that, as our influence metric increases, so does the probability for the use of *gij bent*.
+This means that the more influential a speaker is in the Twitter network, the more likely they are to use the new, innovative *gij bent* form.
+[Todo Julie uitleg hoe en waarom dit zo is]
+
 [network effect explanation]

### 2024-11-28 paper/paper.qmd
Fix some Quarto cross reference issues

@@
 ```{r #tbl-other-coefficients}
+#| label: tbl-other-coefficients
+#| tbl-cap: "Overview of the controlling predictors predictors, their values and whether they were retained by the elastic net regression" 
 # All other coefficients start with an underscore
@@
 
-```{r linear-regression-model}
+```{r #tbl-linear-predictors}
+#| tbl-cap: "Results of the linear regression analysis. * indicates statistical significance"
 fit <- lm(coefficient ~ gender + dialect + influence, data=coefficients %>% no_unknown_gender())
@@
 
-```{r #tbl-posthoc-test}
+```{r tbl-posthoc-test}
+#| tbl-cap: Results of the `emmeans` posthoc analysis for dialect area. * indicates statistical significance
 posthoc <- emmeans(fit,

### 2024-11-28 analysis/2-analysis.R
Fix some stuff

@@ -30,6 +30,15 @@ coeff %>% no_unknown_gender %>%
   geom_violin() +
   geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
 
+# beeswarm(
+#   coefficient ~ gender,
+#   data=coeff %>% no_unknown_gender %>% filter(coefficient > 0), 
+# )
+
+coeff %>%
+  ggplot(aes(x = dialect, y = coefficient, color = gender)) +
+  geom_point()
+
 coeff %>%
   ggplot(aes(x = dialect, y = coefficient, fill = dialect)) +
   geom_violin() +
@@ -53,11 +62,23 @@ xtabs(~ dialect, coeff %>% filter(coefficient < 0))
 # Find forefront
 #
 brabant_snippet <- coeff %>% filter(dialect == "_is_dialect_Brabants") %>% arrange(coefficient)
+
+brabant_snippet %>% no_unknown_gender %>%
+  ggplot(aes(x = gender, y = coefficient, fill = gender)) +
+  geom_violin() +
+  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
+
 fit <- lm(coefficient ~ log_followers + gender, data=brabant_snippet %>% no_unknown_gender())
 summary(fit)
 
 
-limburg_snippet <- coeff %>% filter(dialect == "_is_dialect_Limburgs") %>% arrange(coefficient)
+non_brabant_snippet <- coeff %>% filter(dialect != "_is_dialect_Brabants") %>% arrange(coefficient)
+
+non_brabant_snippet %>% no_unknown_gender %>%
+  ggplot(aes(x = gender, y = coefficient, fill = gender)) +
+  geom_violin() +
+  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
+
 fit <- lm(coefficient ~ log_followers + gender, data=limburg_snippet %>% no_unknown_gender())
 summary(fit)
 
@@ -90,8 +111,8 @@ xtabs(~ gender, extreme_limburgers)
 extreme_brabanders <- coeff %>% filter(coefficient > 0 & dialect == "_is_dialect_Brabants") %>% no_unknown_gender()
 xtabs(~ gender, extreme_brabanders)
 lm(coefficient ~ gender, data=extreme_brabanders) %>% summary
-mean(extreme_brabanders %>% filter(gender == "_is_gender_female") %>% .$coefficient)
[…]

### 2024-12-09 analysis/0-common.R
Update dependencies

@@ -1,4 +1,7 @@
 library(stringr)
+library(emmeans)
+library(broom)
+library(tidycat)
 
 df <- read.delim("../data/tweets_geo_full.tsv")
 

### 2024-12-09 paper/paper.qmd
Give suggestions for conclusion
Add references

@@
 One of the key ideas from usage-based linguistics is that language is not a system that exists just "by itself".
-Rather, it is widely accepted within this branch that language arises out of the many interactions that language users have with each other [TODO source].
-As such, language becomes a "complex-adaptive system" [TODO source], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users.
+Rather, it is widely accepted within this branch that language arises out of the many interactions that language users have with each other [@keller_language_1994].
+As such, language becomes a "complex-adaptive system" [@ellis_what_2012;@kretzschmar_language_2015], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users.
 While each speaker of a language (be it Dutch, English or Maori) has their own personalised representation of the rules and constraints that they think make up that language, these representations have enough in common in order to warrant talking about a shared "code", or more broadly, a language.
@@
 This situation forces models of language into necessary generalisations.
-Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian A-curve [as suggested by Kretzschmar, TODO].
+Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian [@zipf_psycho-biology_1965] A-curve [as suggested by @kretzschmar_language_2015].
 The make-up of this curve, with the most popular forms capturing most of the language use anyway, makes it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users.
 Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds.
-We see this, for example, in probabilistic grammar, [todo definition].
+We see this, for example, in probabilistic grammar, the branch of variation studies that investigates how variation reflects competing constraints on linguistic choices [@grafmiller_general_2018].
 Still, on a theoretical level, it is regrettable that models of variation do not start from the lowest common denominator of this variation: the language user.
@@
 Whereas previously it was possible to gauge the linguistic profile of only a small group of people [e.g.
-Milroy, Labov], social media offer linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [TODO source].
+@labov_study_1968;@milroy_belfast_1978], social media offer linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [@vandekerckhove_perception_2007, 255].
 In addition, social media data of course do not provide access to *all* of language for *all* users of a language system; not all utterances are made on social media, nor are all language users active on social media platforms.
@@
 Except for small-scale studies [e.g.
-Milroy & Labov TODO], it has been impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
+@labov_study_1968;@milroy_belfast_1978], it has been impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
 Again, social media offer an opportunity here.
@@
 
-To answer the two research questions stated above, we follow up on a study by Sevenants [TODO] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD).
-To compute the individual variation of different language users, we will use elastic net regression, a regression analysis technique pioneered in [todo].
+To answer the two research questions stated above, we follow up on a study by Sevenants [@sevenants_zijt_2024] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD).
+To compute the individual variation of different language users, we will use elastic net regression, a technique suited to determining individual variation.
 First, we will introduce the *gij bent* CBD linguistic innovation.
@@
 Dutch as it is spoken in Belgium has evolved strongly since the second half of the 20^th^ century.
-Until deep in the 20^th^ century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [Auer 2005 TODO].
+Until deep in the 20^th^ century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [@auer_europe_2005].
 This means that the Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
@@
 
-At the start of the 21^st^ century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [again Auer 2005].
+At the start of the 21^st^ century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [@auer_europe_2005].
 In between the dialects and standard language, new language types had appeared, among which so-called "regiolects" (above the dialects) and "regional standards" (below standard language).
@@
 
-Research by [mezelf lol TODO] has shown that *gij bent* most likely originated in dialects from the northern Antwerp province in Flanders, and then spread to other parts of the Brabantian dialect area.[^brabants] The reason for the spread from this area is argued to lie in the function of *gij bent*.
+Research by @sevenants_zijt_2024 has shown that *gij bent* most likely originated in dialects from the northern Antwerp province in Flanders, and then spread to other parts of the Brabantian dialect area.[^brabants] The reason for the spread from this area is argued to lie in the function of *gij bent*.
 The *jij bent* from standard language might feel too formal, while the *gij zijt* from dialects might feel too blunt.
-*Gij bent* strikes a balance between the two: it has colloquial roots through Flemish *gij*, but benefits from the prestige associated with standard language [todo referentie] through standard *bent*.
+*Gij bent* strikes a balance between the two: it has colloquial roots through Flemish *gij*, but benefits from the prestige associated with standard language [@impe_vlamingen_2007] through standard *bent*.
 In addition, both regional, formality and gender effects were found:
@@
 [^brabants]: Brabants is the dialect area coinciding, mostly, with the Flemish provinces "Vlaams-Brabant" and "Antwerp".
-It is said to be the driving force behind CBD, but this claim is disputed [todo Lybaert reference].
+It is said to be the driving force behind CBD, but this claim is disputed [@ghyselen_verticale_2016].
 
@@
 
-As this study is a follow-up on the *gij bent* study by [mezelf TODO], we will re-use the dataset used in that study.
+As this study is a follow-up on the *gij bent* study by @sevenants_zijt_2024, we will re-use the dataset used in that study.
 The dataset contains [TODO infix] social media posts from Belgium on the Twitter platform (now X).
@@
 The tweets are tagged for the Flemish dialect region to which each tweet author belongs.
-In addition, gender information was estimated for each tweet author using [todo].
-Authors for whom gender could not be established were removed, to retain parity with [mezelf TODO].
+In addition, gender information was estimated for each tweet author using *gender-from-name-r* [@sevenants_gender_2024].
+Authors for whom gender could not be established were removed, to retain parity with @sevenants_zijt_2024.
 The dataset also contains a formality distinction for each tweet ("more formal", "more informal"), based on whether a tweet interacts with other people.
@@
 
-In order to operationalise this computation of individual variation, we made use of elastic net regression [todo].
-Elastic net regression is an extension of more "traditional" regression techniques [see 2015 Gries, todo].
+In order to operationalise this computation of individual variation, we made use of elastic net regression [@friedman_regularization_2010].
+Elastic net regression is an extension of more "traditional" regression techniques [discussed in @gries_most_2015].
 Its main innovation is that it uses an extra "penalty" term, which prevents model coefficients, the values associated with model predictors, from growing too large.
@@
 with mixed models).
-For additional details on elastic net regression for linguistics, see [mezelf geaccepteerd leuk].
+For additional details on elastic net regression for linguistics, see @sevenants_elastic_to_appear.
 
@@
 In our model, we estimated coefficients for each language user separately by treating those language users as individual predictors.
-Because we also included all the predictors from [sevenants todo] in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
+Because we also included all the predictors from @sevenanst_zijt_2024 in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
 Due to the multifactorial control characteristic[^multifactoriality] of regression analysis, this makes it so each individual speaker's coefficient becomes a measure of the variation that is not explained on the basis of the more general predictor terms, i.e.
@@
 
-For our analysis, we used ElasticToolsR [todo mezelf], a package for the R language [todo] which simplifies running elastic net regression models.
+For our analysis, we used ElasticToolsR [@sevenants_elastic_2024], a package for the R language [@r_language_2021] which simplifies running elastic net regression models.
 
@@
 We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*.
-Compared to [mezelf todo], some predictors have more subtle effects.
+Compared to @sevenants_zijt_2024, some predictors have more subtle effects.
 Especially the distance correction and the formality distinction correction are smaller.
-We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- [mezelf todo] used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in [mezelf todo] will now be attributed to individual variation.
+We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- @sevenants_zijt_2024 used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in  @sevenants_zijt_2024 will now be attributed to individual variation.
 Still, broadly speaking, the results remain comparable.
@@
 Secondly, we see that the most extreme innovative corrections in the plot stem from men, while the most extreme conservative corrections stem from women.
-This is peculiar, in the sense that this pattern "reverses" what we know from from [mezelf todo] and @sec-controlling-predictors.
+This is peculiar, in the sense that this pattern "reverses" what we know from from @sevenants_zijt_2024 and @sec-controlling-predictors.
 However, keep in mind that the plot shows *corrections* on top of *expectations*.
@@
 Perhaps they they live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
-To answer this question, we built a Generalised Additive Model or GAM [todo ref].
+To answer this question, we built a Generalised Additive Model or GAM [@hastie_generalized_1987].
 A GAM can fit smooth curves to "wavy" data.
@@
 In the GAM plot, we see that the northern Antwerp region is specifically innovative in contrast to an already innovative dialect region, Brabant.
-This is expected from the results by [mezelf todo].
+This is expected from the results by @sevenants_zijt_2024.
 What is especially interesting given our interest in the innovators in the non-Brabant regions, is that we indeed see that areas closer to the Brabant border show corrections that tend more towards the innovative variant.
 In addition, we also see that there seems to be an additional horizontal diffusion pattern, where the more innovative variant seems to spread from east to west in the east and from west to east in the west.
-This pattern remained invisible in the original study by [mezelf todo].
-Computer simulations have shown that border-adjacent speakers can play an important role as gatekeepers of innovations, since their hybrid identity can form a "bridge" through which innovations can be passed on [todo OOK mezelf].
+This pattern remained invisible in the original study.
+Computer simulations have shown that border-adjacent speakers can play an important role as gatekeepers of innovations, since their hybrid identity can form a "bridge" through which innovations can be passed on [@sevenants_neighbours_2021].
 In a sense, the horizontal positive variation coefficient pattern shows the pathway that *gij bent* might take in the future in order to break through in these other dialect regions.
@@
 Firstly, for gender, we see a "reversal" pattern, where typical behaviour is not shared across the entire gender group.
-Secondly, we see a wave-like [todo wave linguistics] horizontal diffusion pattern in the non-Brabant dialect regions, even in regions which, in the general analysis, are thought to be rather conservative.
+Secondly, we see a wave-like [@francois_trees_2014] horizontal diffusion pattern in the non-Brabant dialect regions, even in regions which, in the general analysis, are thought to be rather conservative.
 Though speakers are of course free to use whatever forms they want, how they deviate from expectations is not random.
@@
 
-Our influence metric is based on the priming ratio from [mezelf geaccepteerd leuk] and hinges on logarithm and Laplace smoothing (TODO).
+Our influence metric is based on the priming ratio from @sevenants_elastic_to_appear and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013].
 The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts.
@@
 In addition, we wanted to know whether there are also differences *between* the non-Brabant dialact areas.
-To investigate this, we ran a post-hoc analysis through emmeans (TODO).
+To investigate this, we ran a post-hoc analysis through emmeans [@emmeans].
 In this post-hoc analysis, we check for each dialect area pair whether there are significant differences in individual variation between the two.
@@
 ## Conclusion
+
+- [algemeen idee van de individuele variatie]
+- [conclusies voor tussentaal]
+- [idee dat je op deze manier ook kunt vaststellen in welke fase van de verspreiding een fenomeen zit]

### 2024-12-09 paper/paper.qmd
Fix some reference mistakes

@@
 In our model, we estimated coefficients for each language user separately by treating those language users as individual predictors.
-Because we also included all the predictors from @sevenanst_zijt_2024 in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
+Because we also included all the predictors from @sevenants_zijt_2024 in our analysis, these more general predictors (gender, dialect region, distance from northern Antwerp, formality) form the "expectation" for each specific speaker.
 Due to the multifactorial control characteristic[^multifactoriality] of regression analysis, this makes it so each individual speaker's coefficient becomes a measure of the variation that is not explained on the basis of the more general predictor terms, i.e.

### 2024-12-09 paper/paper.qmd
Add Geeraerts reference to lects
Add piece about power law distributions and Barabasi

@@
 
-[^lects]: i.e. "lects", TODO Geeraerts
+[^lects]: For example, one of the language varieties or "lects", defined as "dialects, regiolects, national varieties, registers, styles, idiolects, whatever" [@geeraerts_lectal_2005, 168]
 
@@
 Humans are embedded in larger social networks, which are formed according to a so-called "power law".
-[uitleg scale-free netwerk]
+This means the network has a small number of people with a large number of connections, supplemented by many people who have relatively few connections [@barabasi_emergence_1999].
+
 Linguistically, the effects of networks has been studied before [stuk Julie].

### 2024-12-09 paper/paper.qmd
Update introduction

@@
 First, we will introduce the *gij bent* CBD linguistic innovation.
-Then, we will describe how we modelled the linguistic profiles of the individual user with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study.
+Then, we will introduce the dataset and describe how we modelled the linguistic profiles of the individual users with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study.
 Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.
-TODO nakijken of dit nog klopt
 

### 2024-12-09 paper/paper.qmd
Rework diglossia treatment

@@
 Dutch as it is spoken in Belgium has evolved strongly since the second half of the 20^th^ century.
-Until deep in the 20^th^ century, the language situation of Dutch in  Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [@auer_europe_2005].
+In the largest part of the 20^th^ century, the language situation of Dutch in Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [@auer_europe_2005].
 This means that the Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
 These two were the language modes available to speakers of Dutch.
-From the XXXies TODO onwards, a large-scale language policy campaign attempted to teach those speakers who mastered only their local dialect the standard language.
+A large-scale language policy campaign at the timed attempted to teach those speakers who mastered only their local dialect the standard language.
 While these efforts were well intended, the imposition of a "foreign" standard language -- the standard was imported from the Netherlands -- were met with limited enthusiasm by language users in Flanders.

### 2024-12-09 paper/paper.qmd
Add origin of English term CBD
Add more 'tussentaal' references

@@
 More generally, however, a new term was coined: *tussentaal*, which roughly translates to "interlanguage".
-In this article, we will use the term defined by TODO, "Colloquial Belgian Dutch" or CBD.
+In this article, we will use the English term as defined by @vandekerckhove_cbd_2005: "Colloquial Belgian Dutch" or CBD.
 
@@
 The presence of region-specific features means that CBD is not a monolithic language variety, but rather sounds different across all places in Flanders.
-This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [todo citaties Zenner].
+This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [i.e.
+@geeraerts_een_2000;@taeldeman_zich_2008].
 

### 2024-12-09 paper/paper.qmd
Add numbers about the dataset size

@@
 As this study is a follow-up on the *gij bent* study by @sevenants_zijt_2024, we will re-use the dataset used in that study.
-The dataset contains [TODO infix] social media posts from Belgium on the Twitter platform (now X).
+The dataset contains `r num_tweets %>% formatn` social media posts from Belgium on the Twitter platform (now X).
 These tweets either contain the traditional *gij zijt* or the innovative *gij bent* construction.
@@
 We did this in order to guarantee a stable estimation of each speaker's language use.
-After all filtering operations, we were left with TODO tweets by TODO unique authors.
+After all filtering operations, we were left with `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` unique authors.
 

### 2024-12-09 analysis/0-common.R

@@ -5,6 +5,8 @@ library(tidycat)
 
 df <- read.delim("../data/tweets_geo_full.tsv")
 
+num_tweets <- dim(df)[1]
+
 MIN_TWEET_THRESHOLD = 10
 
 # Make sure the factor levels are set up so *bent* is the non-default level
@@ -45,6 +47,9 @@ colnames(df)[colnames(df) == "norm_long"] <- "long"
 user_id_counts <- table(df$user_id)
 df <- subset(df, user_id %in%
               names(user_id_counts[user_id_counts >= MIN_TWEET_THRESHOLD]))
+
+num_tweets_filtered <- dim(df)[1]
+num_users_filtered <- length(unique(df$user_id))
 
 # Only one tweet per user
 one_user_one_tweet <- function(df) {

### 2024-12-09 paper/paper.qmd
Finish discussion of control variables

@@
 
-In general, the control variable results are comparable to the results from [mezelf].
+In general, the control variable results are comparable to the results from @sevenants_zijt_2024.
 The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections).
-We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo).
+We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit only very slightly).
 We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*.

### 2024-12-09 paper/paper.qmd
Add GAM equation

@@
 At the same time, the distributions between men and women are still similar enough that we likely cannot speak of distinctly different profiles.
-We will come back to this in our regression model of the coefficients in section TODO.
+We will come back to this in our regression model of the coefficients in @sec-regression.
 
@@
 If extrapolated to two dimensions, it allows one to create "weatherman-like" heatmaps for linguistic data.
-In this case, we modelled the elastic net coefficients on the basis of the latitude and longitude values associated with the places in the profiles of the Twitter users, according to the following equation:
+In this case, we modelled the elastic net coefficients on the basis of the latitude and longitude values associated with the places in the profiles of the Twitter users, in addition to the interaction of the two axes ("tensor smooth", $te$).
+This gives rise to the following equation:
 
-todo equation
+$$
+\text{construction} \sim s(\text{longitude}) + s(\text{latitude}) + te(\text{longitude}, \text{latitude})
+$$
 
@@
 
-#### Network effects
+#### Network effects {#sec-regression}
 

### 2024-12-09 paper/paper.qmd
Add reference to introduction

@@
 
-## Introduction {#sec:introduction}
+## Introduction {#sec-introduction}
 
@@
 
-As mentioned in INTRODUCTION TODO, the networked aspect of social media data provides an opportunity for researchers to investigate which people use what variant, and what that says about the diffusion of a new variant.
+As mentioned in @sec-introduction, the networked aspect of social media data provides an opportunity for researchers to investigate which people use what variant, and what that says about the diffusion of a new variant.
 Since our dataset comes from the Twitter platform, we also dispose of metrics which define a user's relative popularity on the platform.

### 2024-12-09 paper/paper.qmd
Further specifiy laplace equation
Explain difference between lurkers and posters

@@
 The idea of the metric is that users who have a large number of followers, yet follow few people themselves, have a larger relative influence than users without this asymmetry.
-Our influence metric is shown in Equation TODO.
+Our influence metric is shown in the following equation:
 
@@
 users who have more followers than they themselves follow people.
-This is expected, since [todo parlee over disparity tussen posters en lurkers].
+This is expected, since generally speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006].
+Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.
 

### 2024-12-09 paper/paper.qmd
Remove a TODO
Add refer back to group variation section

@@
 
-#### Variation patterns among groups
+#### Variation patterns among groups {#sec-group-variation}
 
@@
 Are they are the forefront of innovation, or are they conservative?
-Depending on what profile we find, we might be able to discern in what phase of diffusion the *gij bent* innovation is situated (see Section TODO).
+Depending on what profile we find, we might be able to discern in what phase of diffusion the *gij bent* innovation is situated.
 
@@
 Bundling all these possible influences in the same model will ensure that we do not accidentally assign variation between language users to the wrong source.
-It will also function as an extra check for the results from Section TODO, as we will now be able to check statistically whether the distinctions we spotted in the visual exploration are statistically significant distinctions.
+It will also function as an extra check for the results from @sec-group-variation, as we will now be able to check statistically whether the distinctions we spotted in the visual exploration are statistically significant distinctions.
 @tbl-linear-predictors gives an overview of the predictors that were used in the linear regression model.

### 2024-12-09 paper/paper.qmd
Add regression value in the text

@@
 First, we look at the intercept of the model.
-Just like in TODO, the intercept here expressed the "default" situation against which further corrections need to be understood.
+Just like in @sec-controlling-predictors, the intercept here expressed the "default" situation against which further corrections need to be understood.
 Here, the intercept expresses a language user ...
@@
 
-Our intercept starts from a value of TODO, which shows a slight bias for innovative behaviour. All further corrections need to be understood relative to this value.
+Our intercept starts from a value of `r fit %>% tidy %>% filter(term == "(Intercept)") %>% .$estimate %>% formatd(3)`, which shows a slight bias for innovative behaviour.
+All further corrections need to be understood relative to this value.
 
@@
 We see that the distinction between users who are thought to be male and users who are thought to be female does not reach the significance threshold.
-Therefore, the differences which we discussed in TODO are not different enough to the degree that they are actually distinct.
+Therefore, the differences which we discussed in @sec-group-variation are not different enough to the degree that they are actually distinct.
 Still, the fact that the *tendency* is clearly there is still interesting, and the reversal of the extreme values of course still holds.

### 2024-12-09 paper/paper.qmd
Fix posthoc table

@@
   df$contrast <- gsub("[()]", "", df$contrast)
-  df$contrast <- gsub("-", "↔", df$contrast)
+  df$contrast <- gsub(" - ", " ↔ ", df$contrast)
 
@@
 #| fig-cap: A violin plot describing the individual variation coefficients for men and women. A wider figure means more data for that y value.
+coefficients$gender_friendly <- gsub("(_is_gender_)", "", coefficients$gender)
+coefficients$gender_friendly <- factor(coefficients$gender_friendly, levels=c("male", "female"))
+
 coefficients %>%
-  ggplot(aes(x = gender, y = coefficient, fill = gender)) +
+  ggplot(aes(x = gender_friendly, y = coefficient, fill = gender_friendly)) +
   geom_violin() +
+  xlab("gender") +
+  guides(fill=guide_legend(title="gender")) +
   geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
@@
 #| fig-cap: A violin plot describing the individual variation coefficients by region. A wider figure means more data for that y value.
+coefficients$dialect_friendly <- gsub("(_is_dialect_)", "", coefficients$dialect)
+#coefficients$gender_friendly <- factor(coefficients$gender_friendly, levels=c("male", "female"))
+
 coefficients %>%
-  ggplot(aes(x = dialect, y = coefficient, fill = dialect)) +
+  ggplot(aes(x = dialect_friendly, y = coefficient, fill = dialect_friendly)) +
   geom_violin() +
+  xlab("dialect area") +
+  guides(fill=guide_legend(title="dialect area")) +
   geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
@@
 fit <- lm(coefficient ~ gender + dialect + influence, data=coefficients %>% no_unknown_gender())
-fit %>% format_table()
+coefficients_lm_df <- fit %>% format_table()
+
+coefficients_lm_df$term <- gsub("(gender_)", "", coefficients_lm_df$term)
+coefficients_lm_df$term <- gsub("(_is_dialect_)", "", coefficients_lm_df$term)
+
+coefficients_lm_df
 ```
@@
 
-posthoc %>% format_posthoc_table()
+posthoc_df <- posthoc %>% format_posthoc_table()
+posthoc_df$contrast <- gsub("(_is_dialect_)", "", posthoc_df$contrast)
+
+posthoc_df
 ```

### 2024-12-09 paper/paper.qmd
Fix West Flanders correction

@@
 The regression analysis assumes a zero distance from Antwerp from the intercept, but this does not make sense for dialect areas other than Brabant.
-Therefore, if we apply the extra corrections expressed in "distance from northern Antwerp", we get the expected negative correction towards the conservative form (`r 121 * -0.017`).
+Therefore, if we apply the extra corrections expressed in "distance from northern Antwerp", we get the expected negative correction towards the conservative form (`r (121 * coefficients_full %>% filter(feature == "_distance_from_antwerp") %>% .$coefficient) %>% formatd(3)`).
 Still, the *gij* pronoun is quite rare in this area, so the West-Flemish results should be treated with caution.

### 2024-12-09 paper/paper.tex
generally > broadly

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod,
  oneside]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=1in,marginparwidth=2.0666666666667in,textwidth=4.1333333333333in,marginparsep=0.3in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tablesignature}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={gij bent 2},
  pdfauthor={Anthe Sevenants; Julie Nijs},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{gij bent 2}
\author{Anthe Sevenants \and Julie Nijs}
\date{}

\begin{document}
\maketitle
\begin{abstract}
TODO
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}

\section{Introduction}\label{sec-introduction}

One of the key ideas from usage-based linguistics is that language is
not a system that exists just ``by itself''. Rather, it is widely
accepted within this branch that language arises out of the many
interactions that language users have with each other (Keller 1994). As
such, language becomes a ``complex-adaptive system'' (Ellis 2012;
Kretzschmar 2015), a system without a single authoritative control,
constructed through the simple yet numerous interactions of its
components, language users. While each speaker of a language (be it
Dutch, English or Maori) has their own personalised representation of
the rules and constraints that they think make up that language, these
representations have enough in common in order to warrant talking about
a shared ``code'', or more broadly, a language.

When it comes to research of said shared code, things become more
complicated. It is impossible for researchers to know the complete code
of \emph{all} language users in a language system. This situation forces
models of language into necessary generalisations. Generalisation is a
valid strategy, as most linguistic variation, when tallied at large,
will lead to a Zipfian (Zipf 1965) A-curve (as suggested by Kretzschmar
2015). The make-up of this curve, with the most popular forms capturing
most of the language use anyway, makes it so the ``general'' behaviour
of language variation that is typically captured in corpora also
represents a fair share of what would be the individual code of most
language users. Of course, there are factors influencing what language
forms are used,\sidenote{\footnotesize For example, one of the language varieties or
  ``lects'', defined as ``dialects, regiolects, national varieties,
  registers, styles, idiolects, whatever'' (Geeraerts 2005, 168)} but
broadly speaking, this generalisation holds. We see this, for example,
in probabilistic grammar, the branch of variation studies that
investigates how variation reflects competing constraints on linguistic
choices (Grafmiller et al. 2018). Still, on a theoretical level, it is
regrettable that models of variation do not start from the lowest common
denominator of this variation: the language user.

Contrastively, the advent of social media offers a unique opportunity
for variationist research. Social media platforms offer an insight into
the language systems of a large number of people. Whereas previously it
was possible to gauge the linguistic profile of only a small group of
people (e.g. Labov et al. 1968; Milroy and Milroy 1978), social media
offer linguistic variation at an unprecedented scale.\sidenote{\footnotesize More
  recently, the release of the C-Clamp corpus {[}todo{]} offers a
  diachronic insight into the language use of Dutch-speaking writers
  from XXX to XXX. The historical nature of this corpus, however, limits
  its use for research into contemporary language variation phenomena.}
While one should not consider spoken and written social media as
equivalent, social media language has nonetheless proven a useful proxy
for the former (Vandekerckhove and Cuvelier 2007, 255). In addition,
social media data of course do not provide access to \emph{all} of
language for \emph{all} users of a language system; not all utterances
are made on social media, nor are all language users active on social
media platforms. Nevertheless, social media platforms bring us closer to
the idea of studying language \emph{inside out}, starting from
individual language users' variation, even if it is only for a single
alternation among a subset of language users. This brings us to the
first research question of this study:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  What affordances does a focus on individual variation bring us in the
  context of alternation research, especially in contrast to
  traditional, aggregated alternation research?
\end{enumerate}

{[} @ Julie: misschien hier een stuk over het reeds bestaande onderzoek
naar individuele variatie. hoeft niet veel te zijn maar nu staat er
niets en dat is misschien niet top {]}

Another aspect of of the complex-adaptive system of language are the
connections between people. Humans are embedded in larger social
networks, which are formed according to a so-called ``power law''. This
means the network has a small number of people with a large number of
connections, supplemented by many people who have relatively few
connections (Barabasi 1999).

Linguistically, the effects of networks has been studied before {[}stuk
Julie{]}.

\begin{itemize}
\tightlist
\item
  leaders / loaners
\item
  gedrag van centrale figuren
\item
  alle andere dingen die interessant zouden kunenn zijn
\end{itemize}

Except for small-scale studies (e.g. Labov et al. 1968; Milroy and
Milroy 1978), it has been impossible to get an elaborate insight into
the social relationships of people on a large scale, let alone how these
relationships relate to language. Again, social media offer an
opportunity here. While it is not practical to get a full network of
\emph{all} social media users, we \emph{can} get information on how
``connected'' a particular user is. Through metrics like ``followers''
and ``following'', we know how many connections social media users have.
This allows us to get an idea of the centrality of a user in the larger
social media network, even if we do not know the full network itself.
This brings us to the second research question in this study:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  How can we leverage the network implicit in social media data to learn
  more about the spread of linguistic innovations?
\end{enumerate}

To answer the two research questions stated above, we follow up on a
study by Sevenants (Sevenants 2024a) about \emph{gij bent}, a linguistic
innovation concerning the second person of `to be' in Colloquial Belgian
Dutch (CBD). To compute the individual variation of different language
users, we will use elastic net regression, a technique suited to
determining individual variation. First, we will introduce the \emph{gij
bent} CBD linguistic innovation. Then, we will introduce the dataset and
describe how we modelled the linguistic profiles of the individual users
with regard to this innovation using elastic net, and why we need this
specific technique to answer the questions we have in this study. Next,
we will show the results of our analyses, and discuss what consequences
they have for usage-based alternation research in general.

\section{\texorpdfstring{The case of \emph{gij
bent}}{The case of gij bent}}\label{the-case-of-gij-bent}

This study focusses on \emph{gij bent}, an innovation within Colloquial
Belgian Dutch (CBD). Before we explain what this innovation is about, we
will first explain the general language situation of Dutch in Belgium.

\subsection{Dutch in Belgium}\label{dutch-in-belgium}

Dutch as it is spoken in Belgium has evolved strongly since the second
half of the 20\textsuperscript{th} century. In the largest part of the
20\textsuperscript{th} century, the language situation of Dutch in
Flanders, the Dutch-speaking part of Belgium, could best be described as
a \emph{diglossia} (Auer 2005). This means that the Dutch was
characterised by a dichotomy between standard language on the one hand,
and dialects on the other hand. These two were the language modes
available to speakers of Dutch. A large-scale language policy campaign
at the timed attempted to teach those speakers who mastered only their
local dialect the standard language. While these efforts were well
intended, the imposition of a ``foreign'' standard language -- the
standard was imported from the Netherlands -- were met with limited
enthusiasm by language users in Flanders. However, this language
campaign was not without effect, albeit not the intended one.

At the start of the 21\textsuperscript{st} century, it had become clear
that Flanders was evolving into a new type of language situation:
\emph{diaglossia} (Auer 2005). In between the dialects and standard
language, new language types had appeared, among which so-called
``regiolects'' (above the dialects) and ``regional standards'' (below
standard language). More generally, however, a new term was coined:
\emph{tussentaal}, which roughly translates to ``interlanguage''. In
this article, we will use the English term as defined by Vandekerckhove
(2005): ``Colloquial Belgian Dutch'' or CBD.

The new variant CBD is characterised by being hard to define. In
general, it is best described as a ``standard-adjacent'', colloquial
form of Belgian Standard Dutch, with both general Flemish elements and
region-specific features added to it on all levels (phonology,
morphology, syntax etc.). The presence of region-specific features means
that CBD is not a monolithic language variety, but rather sounds
different across all places in Flanders. This inherent variability is
intrinsic to its linguistic identity, but frustrating to linguists, who
have been trying to come up with ``defining features'' for decades (i.e.
Geeraerts 2000; Taeldeman 2008).

\subsection{\texorpdfstring{\emph{gij bent}}{gij bent}}\label{gij-bent}

Traditionally in Flanders, if one wishes to say ``you are'' in an
informal way, they would say \emph{gij zijt}. \emph{Gij} marks the
informal second person pronoun that is typical to most Flemish dialects.
\emph{Zijt} is a historic form of \emph{zijn} `to be' that is now
exclusively used with this pronoun. If one wanted to say ``you are'' in
a formal way (i.e.~in standard language), they would say \emph{jij
bent}. \emph{Jij} marks the non-polite, yet formal second person pronoun
in Flanders. \emph{Jij} is more formal than \emph{gij} because the
\emph{jij} pronoun is actually a Netherlandic form that, because it is
foreign, has a different status than \emph{gij}. \emph{Bent} is the
conjugated form that goes along with \emph{jij}. It is also imported
from the Netherlands.

It is clear, then, that these two forms are distinctly different from
each other. However, in CBD, a blend of these two forms has appeared:
\emph{gij bent}. It combines the \emph{gij} pronoun from \emph{gij zijt}
with the \emph{bent} conjugation known from standard language. \emph{Gij
bent} is a quite literal example of the diaglossia situation, as it
combines \emph{gij} and \emph{bent} from polar opposites of the language
spectrum and meets somewhere in the middle.

Research by Sevenants (2024a) has shown that \emph{gij bent} most likely
originated in dialects from the northern Antwerp province in Flanders,
and then spread to other parts of the Brabantian dialect
area.\sidenote{\footnotesize Brabants is the dialect area coinciding, mostly, with the
  Flemish provinces ``Vlaams-Brabant'' and ``Antwerp''. It is said to be
  the driving force behind CBD, but this claim is disputed (Ghyselen,
  Anne-Sophie 2016).} The reason for the spread from this area is argued
to lie in the function of \emph{gij bent}. The \emph{jij bent} from
standard language might feel too formal, while the \emph{gij zijt} from
dialects might feel too blunt. \emph{Gij bent} strikes a balance between
the two: it has colloquial roots through Flemish \emph{gij}, but
benefits from the prestige associated with standard language (Impe and
Speelman 2007) through standard \emph{bent}. In addition, both regional,
formality and gender effects were found:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  the use of \emph{gij bent} is limited to the Brabant dialect region
  only
\item
  the use of \emph{gij bent} is less likely in more informal contexts
\item
  the use of \emph{gij bent} is more likely for women
\end{enumerate}

While these conclusions are drawn from language use originating from
social media, the analysis itself is very traditional. As in a standard
corpus linguistic study, it generalises over all language at once, as
well as all language users. This leads to blanket statements as the ones
above. As argued before, there is nothing inherently wrong with this
approach, but given the opportunities in social media data, a more
bottom-up approach would be interesting. More specifically, such an
approach would allow us to detect whether certain language users behave
differently from what we would expect given their location or gender.
These deviations from general expectations are now invisible in the
generalising models. In addition, no account was taken of the network
structure hidden in the data, which might reveal more about the forces
and the direction this innovation will take in the future.

\section{Data and methodology}\label{data-and-methodology}

\subsection{Dataset}\label{dataset}

As this study is a follow-up on the \emph{gij bent} study by Sevenants
(2024a), we will re-use the dataset used in that study. The dataset
contains 29,429 social media posts from Belgium on the Twitter platform
(now X). These tweets either contain the traditional \emph{gij zijt} or
the innovative \emph{gij bent} construction. The tweets are tagged for
the Flemish dialect region to which each tweet author belongs. In
addition, gender information was estimated for each tweet author using
\emph{gender-from-name-r} (Sevenants 2024b). Authors for whom gender
could not be established were removed, to retain parity with Sevenants
(2024a). The dataset also contains a formality distinction for each
tweet (``more formal'', ``more informal''), based on whether a tweet
interacts with other people. If it does, the idea is that the tweet is
conversation-like and thus more informal. Each tweet also has a unique
(anonymised) identifier, so tweets can be grouped by author. This will
prove especially useful for this study on individual variation, since we
need several tweets in order to gauge the language use of a specific
speaker. For each author, we also know many accounts they follow, and
how many accounts they are followed by. This is a metric that is useful
for our questions about network influences. For our analysis of
individual variation, we retained only those authors who have at least
10 tweets in our dataset. We did this in order to guarantee a stable
estimation of each speaker's language use. After all filtering
operations, we were left with 16,968 tweets by 635 unique authors.

\subsection{Elastic net regression}\label{elastic-net-regression}

To estimate the individual variation among our tweet authors, we would
ideally have a quantitative measure which indicates the deviation of
each user from the expected linguistic behaviour. Authors who do not
deviate would be assigned a (near-)zero value, while those who \emph{do}
deviate would receive either a positive or negative value, depending on
whether they exceed the expectations for their profiles, or actually go
against it. In this way, our measure of individual variation truly
expresses the peculiarities of each individual speaker.

In order to operationalise this computation of individual variation, we
made use of elastic net regression (Friedman, Tibshirani, and Hastie
2010). Elastic net regression is an extension of more ``traditional''
regression techniques (discussed in Gries 2015). Its main innovation is
that it uses an extra ``penalty'' term, which prevents model
coefficients, the values associated with model predictors, from growing
too large. One could think of this as making the model \emph{worse}, but
on purpose. In practice, this model penalty is applied for two reasons.
First, it attempts to prevent overfitting. Too few data points can skew
the estimation of a coefficient, so the penalty is a means to attenuate
predictions in such cases. Second, the model penalty can function as a
way to do variable selection. With elastic net, a coefficient can be
``punished'' to the extent that it nears or equals to zero. With this,
the predictor of that coefficient is disabled outright. We can use this
behaviour to enter many predictors in the same analysis at once, and let
the model decide which ones are actually interesting.

In addition, elastic net leverages ``k-fold cross validation''. This
technique divides the data into several parts and iteratively uses
different parts for training and testing the regression model. This
practice also contributes towards general robustness and the prevention
of overfitting. K-fold cross validation allows us to have hundreds of
predictors in a single analysis, which is a useful property when we want
to track a multitude of language users at the same time. Such a thing
would be impossible with a regular regression analysis on the basis of
mathematical intractability (i.e.~with mixed models). For additional
details on elastic net regression for linguistics, see Sevenants, Van de
Velde, and Speelman (n.d.).

In general, then, elastic net regression lends itself nicely to research
into individual variation. With elastic net, we modelled the presence of
either \emph{zijt} (conservative) or \emph{bent} (innovative) as a
logistic response variable. In our model, we estimated coefficients for
each language user separately by treating those language users as
individual predictors. Because we also included all the predictors from
Sevenants (2024a) in our analysis, these more general predictors
(gender, dialect region, distance from northern Antwerp, formality) form
the ``expectation'' for each specific speaker. Due to the multifactorial
control characteristic\sidenote{\footnotesize Multifactorial control means that the
  analysis takes all predictors into account at the same time. This
  guarantees that variation due to one predictor is not assumed to stem
  from another.} of regression analysis, this makes it so each
individual speaker's coefficient becomes a measure of the variation that
is not explained on the basis of the more general predictor terms,
i.e.~the individual deviation or variation we expressed our desire for
in the previous sections.

For an overview of all predictors included in our model, see
Table~\ref{tbl-predictors}.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
predictor
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
explanation
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
predictor
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
explanation
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
dialect* & the dialect area the tweet poster belongs to (``West
Flemish'', ``East Flemish'', ``Brabantian'', ``Limburgish'') \\
gender & the estimated gender of the tweet poster -- generated
automatically \\
distance from northern Antwerp & the distance of the poster's location
in km from the northern Antwerp area \\
formality & the formality of the tweet -- derived from whether the tweet
author interacts with another user in the tweet \\
user\_id* & a unique (anonymised) identifier for the tweet author --
allows us to know which tweets belong to the same person \\
\caption{An overview of all predictors which will be used in the elastic
net regression. Predictors marked with * receive separate predictors for
each level (for example, separate predictors for each tweet
author).}\label{tbl-predictors}\tabularnewline
\end{longtable}

For our analysis, we used ElasticToolsR (Sevenants 2023), a package for
the R language (R Core Team 2021) which simplifies running elastic net
regression models.

\section{Results}\label{results}

In this section, we will go over the results produced by our elastic net
regression model. We will first look at the predictors included in the
previous study to ensure our model produces comparable results. Then, we
will dive into the predictors describing the behaviour of the individual
language users.

\subsection{Controlling predictors}\label{sec-controlling-predictors}

Table~\ref{tbl-other-coefficients} gives an overview of the ``control''
coefficients that were included in order to have multifactorial control
for the individual variation. Since the innovative \emph{bent} variant
was encoded as outcome ``1'', and the conservative \emph{zijt} was
encoded as outcome ``0'', positive coefficients mean a a correction
towards the innovative variant, while negative corrections mean a
correction towards the conservative variant. These corrections must be
interpreted from the situation expressed in the intercept, a ``reference
situation'' that is defined as follows:

\begin{itemize}
\tightlist
\item
  formal situation (no reply or interaction)
\item
  at distance ``0'' from northern Antwerp
\item
  for users assumed to be male
\end{itemize}

In general, the control variable results are comparable to the results
from Sevenants (2024a). The innovative \emph{gij bent} is more popular
in the Brabant dialect area (positive correction), and less popular in
the other areas (negative corrections). We even see the same anomaly for
the West-Flemish dialect area.\sidenote{\footnotesize The results for the West-Flemish
  dialect area need to be interpreted in conjunction with the ``distance
  from northern Antwerp'' parameter. The regression analysis assumes a
  zero distance from Antwerp from the intercept, but this does not make
  sense for dialect areas other than Brabant. Therefore, if we apply the
  extra corrections expressed in ``distance from northern Antwerp'', we
  get the expected negative correction towards the conservative form
  (-2.079). Still, the \emph{gij} pronoun is quite rare in this area, so
  the West-Flemish results should be treated with caution.} \emph{gij
bent} becomes less popular as we move away from northern Antwerp, and
more informal tweets also correct towards the conservative \emph{gij
zijt} (albeit only very slightly). We still see the expected gender
effect, where tweets assumed to come from women have a higher
probability of the use of \emph{gij bent}. Compared to Sevenants
(2024a), some predictors have more subtle effects. Especially the
distance correction and the formality distinction correction are
smaller. We assume these differences stem from (i) the coefficient
attenuation from the elastic net penalty (ii) a difference in dataset
size -- Sevenants (2024a) used only one tweet per user because of issues
with random effects, which we sidestep by using elastic net regression
(iii) parts of the variation attributed to other predictors in Sevenants
(2024a) will now be attributed to individual variation. Still, broadly
speaking, the results remain comparable. Therefore, we can safely move
on to the discussion of the individual variation.

\begin{longtable}[]{@{}lrl@{}}

\toprule\noalign{}
predictor & coefficient & retained \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
dialect: Brabants & 0.878 & yes \\
gender: female & 0.705 & yes \\
dialect: West-Vlaams & 0.000 & no \\
distance from Antwerp (km) & -0.017 & yes \\
dialect: Oost-Vlaams & -0.081 & yes \\
reply: yes & -0.098 & yes \\
dialect: Limburgs & -1.216 & yes \\

\caption{\label{tbl-other-coefficients}Overview of the controlling
predictors predictors, their values and whether they were retained by
the elastic net regression}

\tabularnewline
\end{longtable}

\subsection{Individual variation}\label{individual-variation}

In this section, we will go over the coefficients that were computed for
each language user. We will first look at the variation patterns
globally, and then zoom in on the differences between different groups
of language users. We will also attempt to model the coefficients in
order to find relations between them.

\subsubsection{Global variation pattern}\label{global-variation-pattern}

First, we will look at the coefficient globally. The density plot of the
variation coefficients in Figure~\ref{fig-general-density} gives a
global overview of the how each language user ``deviates'' from what is
expected given their gender, location etc.. Negative coefficients on the
left side of the plot show deviations of individual language users
towards the conservative \emph{gij zijt}. Positive coefficients on the
right side of the plot show deviations of individual language users
towards the innovative \emph{gij bent}. The middle dotted line marks the
zero coefficient, i.e.~those who do not deviate from the expected norm.
We see that there is a bi-modal distribution in the variation
coefficients. The first distribution shows many slights corrections
towards the conservative form (first bump). The second distribution
shows a smaller number of larger corrections towards the innovative form
(second bump). This bi-modal variation pattern would have remained
invisible in a more traditional regression model.

Note that each of the two different distributions might not consist of a
homogeneous type of people. For example, the innovative corrections
might include people in regions where the innovative form is rarely
used, and who use the innovative form nonetheless. At the same time,
innovative corrections might also stem from people in an already
innovative area who ``out-innovate'' the expectations, using the
innovative form even more often than is expected. We will attempt to
tease out this distinction in the next section.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-general-density-1.pdf}

}

\caption{\label{fig-general-density}A density plot describing the
individual variation coefficients in our dataset. The left side of the
plot (negative coefficients) shows corrections towards the conservative
form, the right side of the plot (positive coefficients) shows
corrections towards the innovative form.}

\end{figure}%

\subsubsection{Variation patterns among
groups}\label{sec-group-variation}

\paragraph{Gender}\label{gender}

Next, we will look at the patterns of variation among different groups.
Figure~\ref{fig-gender-violin} shows the distribution of variation
coefficients between men and women. There are two key points. First, we
see that men and women have comparable profiles, with the same bi-modal
trend seen in the general coefficients overview. We will address this
bi-modality in the section on dialect variation patterns.

Secondly, we see that the most extreme innovative corrections in the
plot stem from men, while the most extreme conservative corrections stem
from women. This is peculiar, in the sense that this pattern
``reverses'' what we know from from Sevenants (2024a) and
Section~\ref{sec-controlling-predictors}. However, keep in mind that the
plot shows \emph{corrections} on top of \emph{expectations}. Though
there are general trends that dictate a certain preference for men or
women, this does not mean that \emph{all} individuals from that group
follow that same pattern. Figure~\ref{fig-gender-violin} shows this
reversal: there are ample outlier speakers who deviate from what is
typically expected from their gender, and this also highlights the need
to be cautious when making generalisations in this regard. At the same
time, the distributions between men and women are still similar enough
that we likely cannot speak of distinctly different profiles. We will
come back to this in our regression model of the coefficients in
Section~\ref{sec-regression}.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-gender-violin-1.pdf}

}

\caption{\label{fig-gender-violin}A violin plot describing the
individual variation coefficients for men and women. A wider figure
means more data for that y value.}

\end{figure}%

\paragraph{Dialect}\label{dialect}

Next, we look at the dispersion of variation by Flemish dialect region
in Figure~\ref{fig-region-violin}. Here, we do not see a ``reversal''
pattern, in contrast to Figure~\ref{fig-gender-violin}. There seem to be
two variation profiles: a Brabant variation profile, and a non-Brabant
variation profile. The Brabant variation profile shows how in the
Brabant dialect region, there is a slight preference for innovation at
the upper end of the coefficient values, with declining coefficents
towards conserative corrections. In the three non-Brabant regions, we
see that there are some innovators, but they are generally few. In these
dialects, the values gravitate towards more conservative corrections.
With these results, we have an explanation for the bi-modal nature of
Figure~\ref{fig-general-density}: the first distribution, centred
\emph{below} zero, consists mostly of language users from non-Brabant
dialect areas who are even more conservative than we expect from their
region, and therefore correct ``downwards''. The second distribution,
centred \emph{above} zero, consists mostly of eager innovators from the
already innovative Brabant dialect area. As avid users of the innovative
form, they correct ``upwards'' in our plots.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-region-violin-1.pdf}

}

\caption{\label{fig-region-violin}A violin plot describing the
individual variation coefficients by region. A wider figure means more
data for that y value.}

\end{figure}%

We see in Figure~\ref{fig-region-violin} that, while they are few,
innovators in non-Brabant dialect areas \emph{do} exist. One might
wonder what the profile of these rare innovators is. Perhaps they they
live close to the border in their specific dialect regions, and are
therefore ``atypically'' innovative for their region. To answer this
question, we built a Generalised Additive Model or GAM (Hastie and
Tibshirani 1987). A GAM can fit smooth curves to ``wavy'' data. If
extrapolated to two dimensions, it allows one to create
``weatherman-like'' heatmaps for linguistic data. In this case, we
modelled the elastic net coefficients on the basis of the latitude and
longitude values associated with the places in the profiles of the
Twitter users, in addition to the interaction of the two axes (``tensor
smooth'', \(te\)). This gives rise to the following equation:

\[
\text{construction} \sim s(\text{longitude}) + s(\text{latitude}) + te(\text{longitude}, \text{latitude})
\]

We will immediately shift towards the visual interpretation of the GAM
in TODO. Dark blue colours show corrections towards the conservative
variant, whereas light yellow colours show corrections towards the
innovative variant. Beware to keep in mind, however, that these
corrections are to be interpreted against the expected behaviour in that
specific dialect region. In the GAM plot, we see that the northern
Antwerp region is specifically innovative in contrast to an already
innovative dialect region, Brabant. This is expected from the results by
Sevenants (2024a). What is especially interesting given our interest in
the innovators in the non-Brabant regions, is that we indeed see that
areas closer to the Brabant border show corrections that tend more
towards the innovative variant. In addition, we also see that there
seems to be an additional horizontal diffusion pattern, where the more
innovative variant seems to spread from east to west in the east and
from west to east in the west. This pattern remained invisible in the
original study. Computer simulations have shown that border-adjacent
speakers can play an important role as gatekeepers of innovations, since
their hybrid identity can form a ``bridge'' through which innovations
can be passed on (Sevenants and Speelman 2021). In a sense, the
horizontal positive variation coefficient pattern shows the pathway that
\emph{gij bent} might take in the future in order to break through in
these other dialect regions.

TODO figure

In general, then, we see that there are two trends in the variation
coefficients. Firstly, for gender, we see a ``reversal'' pattern, where
typical behaviour is not shared across the entire gender group.
Secondly, we see a wave-like (François 2014) horizontal diffusion
pattern in the non-Brabant dialect regions, even in regions which, in
the general analysis, are thought to be rather conservative. Though
speakers are of course free to use whatever forms they want, how they
deviate from expectations is not random.

{[}violin plots{]}

\subsubsection{Network effects}\label{sec-regression}

As mentioned in Section~\ref{sec-introduction}, the networked aspect of
social media data provides an opportunity for researchers to investigate
which people use what variant, and what that says about the diffusion of
a new variant. Since our dataset comes from the Twitter platform, we
also dispose of metrics which define a user's relative popularity on the
platform. The first metric, ``Followers'', tallies how many other users
want to see a user's posts appear in their own social media feed. Users
with a large number of followers have a broad reach, and therefore have
the possibility to be influential in their language use. The second
metric, ``Following'', states how many other people's posts a user wants
to see in their social media feed. Users who follow a large number of
other users have the opportunity of being exposed to a larger linguistic
pallette -- though this need not necessarily be the case.

To assess the influence of the users in our dataset within the larger
Twitter network, we devised a metric which is based on the ratio between
``Followers'' and ``Following''. The idea of the metric is that users
who have a large number of followers, yet follow few people themselves,
have a larger relative influence than users without this asymmetry. Our
influence metric is shown in the following equation:

\[
\log{
  \frac{
    \text{\# followers} + 0.001
  } {
    \text{\# following} + 0.001
  }
}
\]

Our influence metric is based on the priming ratio from Sevenants, Van
de Velde, and Speelman (n.d.) and hinges on logarithm and Laplace
smoothing (Brysbaert and Diependaele 2013). The logarithm is a key
operation in order to compress the wide numeric range found in follower
and following counts. Where some users have thousands of followers, some
only have a few. The use of the logarithm scales this discrepancy down.
In addition, we use Laplace smoothing in order to avoid division by
zero, in the event that users do not follow other users. The mean
influence value among our speakers is 0.30 (median 0.28). The boxplot in
Figure~\ref{fig-influence} shows that our dataset generally consists of
more influential figures, i.e.~users who have more followers than they
themselves follow people. This is expected, since generally speaking,
90\% of social media users only read, but never post themselves (Nielsen
2006). Since our dataset consists of posts, it makes sense that our
dataset mainly engages with the other 10\%, the active users.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-influence-1.pdf}

}

\caption{\label{fig-influence}}

\end{figure}%

In our case, we want to know how the language users who are thought to
be influential in our network behave. Are they are the forefront of
innovation, or are they conservative? Depending on what profile we find,
we might be able to discern in what phase of diffusion the \emph{gij
bent} innovation is situated.

To answer this question, we built a common linear regression model. We
model the coefficients in term of the influence of the users, but we
also supplement our analysis with the dialect and gender distinctions we
discussed earlier. Bundling all these possible influences in the same
model will ensure that we do not accidentally assign variation between
language users to the wrong source. It will also function as an extra
check for the results from Section~\ref{sec-group-variation}, as we will
now be able to check statistically whether the distinctions we spotted
in the visual exploration are statistically significant distinctions.
Table~\ref{tbl-linear-predictors} gives an overview of the predictors
that were used in the linear regression model.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
predictor
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
explanation
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
predictor
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
explanation
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
dialect & the dialect area the tweet poster belongs to (``West
Flemish'', ``East Flemish'', ``Brabantian'', ``Limburgish'') \\
gender & the estimated gender of the tweet poster -- generated
automatically \\
influence & a metric expressing the relative influence of a language
user within the Twitter network \\
\caption{An overview of all predictors used in the linear regression
model.}\label{tbl-linear-predictors}\tabularnewline
\end{longtable}

\begin{longtable}[]{@{}llllll@{}}

\toprule\noalign{}
term & coefficient & std. error & t value & p value & \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
(Intercept) & 1.15 & 0.19 & 6.03 & \textless0.01 & * \\
gender: female & -0.31 & 0.21 & -1.46 & 0.1455 & \\
dialect: Limburgs & -1.37 & 0.35 & -3.87 & \textless0.01 & * \\
dialect: Oost-Vlaams & -2.04 & 0.28 & -7.23 & \textless0.01 & * \\
dialect: West-Vlaams & -1.41 & 0.33 & -4.29 & \textless0.01 & * \\
influence & 0.31 & 0.12 & 2.58 & 0.0103 & * \\

\caption{\label{tbl-linear-predictors}Results of the linear regression
analysis. * indicates statistical significance}

\tabularnewline
\end{longtable}

We will first go over the controlling variables we discussed earlier,
and then move on to the influence predictor.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Intercept
\end{enumerate}

First, we look at the intercept of the model. Just like in
Section~\ref{sec-controlling-predictors}, the intercept here expressed
the ``default'' situation against which further corrections need to be
understood. Here, the intercept expresses a language user \ldots{}

\begin{itemize}
\tightlist
\item
  \ldots{} from the Brabant dialect area
\item
  \ldots{} who is assumed to be male
\item
  \ldots{} with an influence of ``zero''
\end{itemize}

Our intercept starts from a value of 1.154, which shows a slight bias
for innovative behaviour. All further corrections need to be understood
relative to this value.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Gender
\end{enumerate}

We see that the distinction between users who are thought to be male and
users who are thought to be female does not reach the significance
threshold. Therefore, the differences which we discussed in
Section~\ref{sec-group-variation} are not different enough to the degree
that they are actually distinct. Still, the fact that the
\emph{tendency} is clearly there is still interesting, and the reversal
of the extreme values of course still holds.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Dialect area
\end{enumerate}

Next, we also see that there are significant differences between the
reference dialect area (Brabant) and all other dialect areas. As was
already clear from the visual inspection of the corrections per dialect
area, we see that in non-Brabant areas, the corrections tend towards the
conservative form, whereas Brabant area corrections are mostly
innovative.

In addition, we wanted to know whether there are also differences
\emph{between} the non-Brabant dialact areas. To investigate this, we
ran a post-hoc analysis through emmeans (Lenth 2024). In this post-hoc
analysis, we check for each dialect area pair whether there are
significant differences in individual variation between the two. We see
in Table~\ref{tbl-posthoc-test} that there are \emph{no} further
differences between the non-Brabant dialect areas. Our assessment of the
two variation profiles was thus correct.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.3824}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1765}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1618}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1176}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1176}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0441}}@{}}

\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
contrast
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
coefficient
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
std. error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
p value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Brabants ↔ Limburgs & 1.37 & 0.35 & 3.87 & \textless0.01 & * \\
Brabants ↔ Oost-Vlaams & 2.04 & 0.28 & 7.23 & \textless0.01 & * \\
Brabants ↔ West-Vlaams & 1.41 & 0.33 & 4.29 & \textless0.01 & * \\
Limburgs ↔ Oost-Vlaams & 0.67 & 0.42 & 1.61 & 0.3713 & \\
Limburgs ↔ West-Vlaams & 0.04 & 0.45 & 0.09 & 0.9998 & \\
Oost-Vlaams ↔ West-Vlaams & -0.64 & 0.40 & -1.60 & 0.3788 & \\

\caption{\label{tbl-posthoc-test}Results of the \texttt{emmeans} posthoc
analysis for dialect area. * indicates statistical significance}

\tabularnewline
\end{longtable}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Network influence
\end{enumerate}

Finally, we look at the network influence parameter. Recall that our
influence predictor expresses the (im)balance between the ``followers''
and ``following'' metrics, with those users who are followed by more
people than they follow themselves being attributed a larger influence.
The regression table in Table~\ref{tbl-linear-predictors} shows that, as
our influence metric increases, so does the probability for the use of
\emph{gij bent}. This means that the more influential a speaker is in
the Twitter network, the more likely they are to use the new, innovative
\emph{gij bent} form. {[}Todo Julie uitleg hoe en waarom dit zo is{]}

{[}network effect explanation{]}

\section{Conclusion}\label{conclusion}

\begin{itemize}
\tightlist
\item
  {[}algemeen idee van de individuele variatie{]}
\item
  {[}conclusies voor tussentaal{]}
\item
  {[}idee dat je op deze manier ook kunt vaststellen in welke fase van
  de verspreiding een fenomeen zit{]}
\end{itemize}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-auer_europe_2005}
Auer, Peter. 2005. {``Europe's Sociolinguistic Unity, or: A Typology of
European Dialect/Standard Constellations.''} \emph{Perspectives on
Variation: Sociolinguistic, Historical, Comparative} 7: 7--42.
\url{https://doi.org/10.1515/9783110909579}.

\bibitem[\citeproctext]{ref-barabasi_emergence_1999}
Barabasi, Albert-Laszlo. 1999. {``Emergence of Scaling in Random
Networks.''} \emph{arXiv.org} 286 (5439): 509--12.
\url{https://doi.org/10.1126/science.286.5439.509}.

\bibitem[\citeproctext]{ref-brysbaert_dealing_2013}
Brysbaert, Marc, and Kevin Diependaele. 2013. {``Dealing with Zero Word
Frequencies: {A} Review of the Existing Rules of Thumb and a Suggestion
for an Evidence-Based Choice.''} \emph{Behavior Research Methods} 45
(2): 422--30.

\bibitem[\citeproctext]{ref-ellis_what_2012}
Ellis, Nick C. 2012. {``What Can We Count in Language, and What Counts
in Language Acquisition, Cognition, and Use?''} In \emph{Frequency
{Effects} in {Language} {Learning} and {Processing}}, edited by Stefan
Th. Gries and Dagmar Divjak, 1:7--34. De Gruyter Mouton.
\url{https://doi.org/10.1515/9783110274059.7}.

\bibitem[\citeproctext]{ref-francois_trees_2014}
François, Alexandre. 2014. {``Trees, {Waves} and {Linkages}: {Models} of
{Language} {Diversification}.''} In \emph{The {Routledge} {Handbook} of
{Historical} {Linguistics}}, edited by Claire Bowern and Evans Bethwyn,
161--89. Routledge. \url{https://doi.org/10.4324/9781315794013.ch6}.

\bibitem[\citeproctext]{ref-friedman_regularization_2010}
Friedman, Jerome, Robert Tibshirani, and Trevor Hastie. 2010.
{``Regularization {Paths} for {Generalized} {Linear} {Models} via
{Coordinate} {Descent}.''} \emph{Journal of Statistical Software} 33
(1): 1--22. \url{https://doi.org/10.18637/jss.v033.i01}.

\bibitem[\citeproctext]{ref-geeraerts_een_2000}
Geeraerts, Dirk. 2000. {``Een Zondagspak? {Het} {Nederlands} in
{Vlaanderen}: Gedrag, Beleid, Attitudes.''} \emph{Ons Erfdeel} 44:
337--44.
\url{https://wwwling.arts.kuleuven.be/qlvl/PDFPublications/01Eenzondagspak.pdf}.

\bibitem[\citeproctext]{ref-geeraerts_lectal_2005}
---------. 2005. {``Lectal Variation and Empirical Data in Cognitive
Linguistics.''} In \emph{Cognitive Linguistics: Internal Dynamics and
Interdisciplinary Interaction}, 32:163--89. Cognitive Linguistics
Research. Berlin: Mouton de Gruyter.
\url{https://doi.org/10.1515/9783110197716.2.163}.

\bibitem[\citeproctext]{ref-ghyselen_verticale_2016}
Ghyselen, Anne-Sophie. 2016. {``{Verticale structuur en dynamiek van het
gesproken Nederlands in Vlaanderen: een empirische studie in Ieper, Gent
en Antwerpen}.''} PhD thesis, {Ghent University}.

\bibitem[\citeproctext]{ref-grafmiller_general_2018}
Grafmiller, Jason, Benedikt Szmrecsanyi, Melanie Röthlisberger, and
Benedikt Heller. 2018. {``General Introduction: {A} Comparative
Perspective on Probabilistic Variation in Grammar.''} \emph{Glossa: A
Journal of General Linguistics} 3 (1).
\url{https://doi.org/10.5334/gjgl.690}.

\bibitem[\citeproctext]{ref-gries_most_2015}
Gries, Stefan Thomas. 2015. {``The Most Under-Used Statistical Method in
Corpus Linguistics: Multi-Level (and Mixed-Effects) Models.''}
\emph{Corpora} 10 (1): 95--125.
\url{https://doi.org/10.3366/cor.2015.0068}.

\bibitem[\citeproctext]{ref-hastie_generalized_1987}
Hastie, Trevor, and Robert Tibshirani. 1987. {``Generalized {Additive}
{Models}: {Some} {Applications}.''} \emph{Journal of the American
Statistical Association} 82 (398): 371--86.
\url{https://doi.org/10.1080/01621459.1987.10478440}.

\bibitem[\citeproctext]{ref-impe_vlamingen_2007}
Impe, Leen, and Dirk Speelman. 2007. {``Vlamingen En Hun (Tussen) Taal:
{Een} Attitudineel Mixed Guise-Onderzoek.''}
\emph{Handelingen-Koninklijke Zuid-Nederlandse Maatschappij Voor Taal-En
Letterkunde En Geschiedenis} 61.

\bibitem[\citeproctext]{ref-keller_language_1994}
Keller, Rudi. 1994. \emph{On {Language} {Change}: {The} {Invisible}
{Hand} in {Language}}. Psychology Press.

\bibitem[\citeproctext]{ref-kretzschmar_language_2015}
Kretzschmar, William A. 2015. \emph{Language and {Complex} {Systems}}.
Cambridge: Cambridge University Press.
\url{https://doi.org/10.1017/CBO9781316179017}.

\bibitem[\citeproctext]{ref-labov_study_1968}
Labov, William et al. 1968. {``A Study of the Non-Standard English of
Negro and Puerto Rican Speakers in New York City.''}

\bibitem[\citeproctext]{ref-emmeans}
Lenth, Russell V. 2024. {``Emmeans: Estimated Marginal Means, Aka
Least-Squares Means.''} \url{https://github.com/rvlenth/emmeans}.

\bibitem[\citeproctext]{ref-milroy_belfast_1978}
Milroy, James, and Lesley Milroy. 1978. {``Belfast: Change and Variation
in an Urban Vernacular.''} \emph{Sociolinguistic Patterns in British
English} 19: 19--36.

\bibitem[\citeproctext]{ref-nielsen_participation_2006}
Nielsen, Jakob. 2006. {``Participation {Inequality}: {The} 90-9-1 {Rule}
for {Social} {Features}.''} \emph{Nielsen Norman Group}.
\url{https://www.nngroup.com/articles/participation-inequality/}.

\bibitem[\citeproctext]{ref-r_language_2021}
R Core Team. 2021. {``R: A Language and Environment for Statistical
Computing.''} Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-sevenants_elastic_2024}
Sevenants, Anthe. 2023. {``ElasticToolsR.''} Zenodo.
\url{https://doi.org/10.5281/zenodo.8113291}.

\bibitem[\citeproctext]{ref-sevenants_zijt_2024}
---------. 2024a. {``{`{Zijt} Gij Dat of Bent Gij Dat?'}: {Een}
Alternantiestudie van de Tweede Persoon Enkelvoud van Zijn in {Vlaamse}
Tussentaal,''} January.
\url{https://doi.org/10.5117/TET2023.2.003.SEVE}.

\bibitem[\citeproctext]{ref-sevenants_gender_2024}
---------. 2024b. {``Gender-from-Name-r.''} Zenodo.
\url{https://doi.org/10.5281/zenodo.14013816}.

\bibitem[\citeproctext]{ref-sevenants_neighbours_2021}
Sevenants, Anthe, and Dirk Speelman. 2021. {``Keeping up with the
Neighbours-an Agent-Based Simulation of the Divergence of the Standard
Dutch Pronunciations in the Netherlands and Belgium.''}
\emph{Computational Linguistics in the Netherlands Journal} 11: 5--26.
\url{https://clinjournal.org/clinj/article/view/118}.

\bibitem[\citeproctext]{ref-sevenants_elastic_to_appear}
Sevenants, Anthe, Freek Van de Velde, and Dirk Speelman. n.d.
{``Investigating Lexical-Semantic Effects on Morphosyntactic Variation
Using Elastic Net Regression.''} \emph{Corpus Linguistics and Linguistic
Theory}, Accepted.

\bibitem[\citeproctext]{ref-taeldeman_zich_2008}
Taeldeman, Johan. 2008. {``Zich Stabiliserende Grammaticale Kenmerken in
{Vlaamse} Tussentaal.''} \emph{Taal En Tongval} 60 (1): 26--50.

\bibitem[\citeproctext]{ref-vandekerckhove_cbd_2005}
Vandekerckhove, Reinhild. 2005. {``Belgian Dutch Versus Netherlandic
Dutch: New Patterns of Divergence? On Pronouns of Address and
Diminutives.''} \emph{Multilingua} 24 (4): 379--97.
\url{https://doi.org/10.1515/mult.2005.24.4.379}.

\bibitem[\citeproctext]{ref-vandekerckhove_perception_2007}
Vandekerckhove, Reinhild, and Poi Cuvelier. 2007. {``The Perception of
Exclusion and Proximity Through the Use of {Standard} {Dutch},
{`Tussentaal'} and Dialect in {Flanders}.''} In \emph{Multilingualism
and Exclusion. {Policy} Practice and Prospects}, 241--56. Studies in
{Language} {Policy} in {South}-{Africa}. Pretoria: Van Schaik
Publishers.

\bibitem[\citeproctext]{ref-zipf_psycho-biology_1965}
Zipf, George Kingsley. 1965. \emph{The {Psycho}-{Biology} of
{Language}}. Cambridge, Massachusetts: MIT Press.

\end{CSLReferences}

\end{document}

### 2024-12-11 paper/paper.qmd
generally > broadly
Change PDF margins

@@
     toc: false
+  pdf:
+    geometry:
+      - top=20mm
+      - left=20mm
+      - right=20mm
+      - bottom=20mm
+      - heightrounded
 editor: source
@@
 number-sections: true
-reference-location: margin
+#reference-location: margin
 csl: chicago-author-date.csl
@@
 users who have more followers than they themselves follow people.
-This is expected, since generally speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006].
+This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006].
 Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.

### 2024-12-11 paper/paper.qmd
Add a suggestion for a conclusion

@@
 
+This article aimed to investigate whether and how speakers deviate from general expectations.
+We focussed on the affordances these deviations, defined as individual variation, can bring for alternation research, as well as what implicit network structures can teach us about the spread of linguistic innovations.
+We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors.
+By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region.
+Through elastic net regression, a modern regression technique, deviations were found for TODO users in the dataset (TODO percent).
+TODO more conservative, TODO more innovative We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects.
+The Brabant region deviates towards the innovative form, the other regions deviate towards the conservative form.
+We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.
+
+The consequences of our findings are twofold.
+In a broad sense, our results show that individual variation exists, and in fact is abundant in our case.
+This illustrates that an important dimension of variation is likely lost in traditional regression models.
+The regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random.
+In a sense, it means that there is "second order variation", variation *within* the variation, so to say.
+The geospatial distribution also provides an opportunity to anticipate upcoming diffusion patterns.
+Of course, we should not treat these patterns as oracles, but they can be useful nonetheless.
+
+The predictive nature of the geospatial distributions bring us to the network analysis of our study.
+Our results show that the socially influential users in our dataset are generally more innovative.
+This might indicate that the diffusion of the innovative *bent* variant is in the TODO phase.
+
 - [algemeen idee van de individuele variatie]

### 2024-12-18 paper/paper.qmd
typo correction and years cclamp added

@@
 
-[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from XXX to XXX.
+[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from 1837 to 1999.
 The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.
@@
 
-Another aspect of of the complex-adaptive system of language are the connections between people.
+Another aspect of the complex-adaptive system of language are the connections between people.
 Humans are embedded in larger social networks, which are formed according to a so-called "power law".

### 2024-12-18 paper/paper.qmd
introduction to individual variation

@@
 
-[ @ Julie: misschien hier een stuk over het reeds bestaande onderzoek naar individuele variatie. hoeft niet veel te zijn maar nu staat er niets en dat is misschien niet top ]
+It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals.
+While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers.
+This is way both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible.
+Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [Nevalainen, Raumolin-Brunberg, and Mannila 2011 TODO].
+While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [Petré and Van de Velde 2018 TODO].
+There is also variation in the language-internal factors influencing language change.
+While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [Fonteyn and Nini 2020 TODO].
+Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [Fonteyn and Petré 2022 TODO].
+Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [Guy 2013; Zenner, Kristiansen, and Geeraerts 2016; Van den Stock et al.
+2024 TODO].
 

### 2024-12-18 paper/paper.qmd
effects of networks

@@
 
-Linguistically, the effects of networks has been studied before [stuk Julie].
+Linguistically, the effects of networks have been studied before.
+Milroy and Milroy [1985 TODO], who base themselves on Granovetter [1973 TODO] and Rogers and Shoemaker [1971 TODO], demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change.
+Strong ties (e.g.
+close friends and family) maintain and reinforce linguistic norms within tight-knit groups, resisting linguistic innovation.
+In contrast, weak ties (e.g.
+acquaintances) form bridges between groups, facilitate the spread of linguistic innovations.
+Weak ties are especially crucial for exposing individuals to linguistic features or patterns that are not present within their immediate, tightly connected group, enabling the flow of new linguistic forms across disparate groups, broadening the reach of linguistic innovations.
+Once exposed to these new forms, individuals connected through weak ties may adopt them and, through their strong ties, introduce them to their close-knit circles.
 

### 2025-08-19 paper/paper.qmd
references added to introduction

@@
 Rather, it is widely accepted within this branch that language arises out of the many interactions that language users have with each other [@keller_language_1994].
-As such, language becomes a "complex-adaptive system" [@ellis_what_2012;@kretzschmar_language_2015], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users.
+As such, language becomes a "complex-adaptive system" [@steels_language_2000;@beckner_language_2009;@ellis_what_2012;@kretzschmar_language_2015], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users.
 While each speaker of a language (be it Dutch, English or Maori) has their own personalised representation of the rules and constraints that they think make up that language, these representations have enough in common in order to warrant talking about a shared "code", or more broadly, a language.
@@
 
-[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from 1837 to 1999.
+[^c-clamp]: More recently, the release of the C-Clamp corpus [@piersoul_150_2021] offers a diachronic insight into the language use of Dutch-speaking writers from 1837 to 1999.
 The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.

### 2025-08-19 paper/paper.qmd
typo fix

@@
 While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers.
-This is way both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible.
+This is why both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible.
 Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [Nevalainen, Raumolin-Brunberg, and Mannila 2011 TODO].

### 2025-08-19 paper/paper.qmd
references added

@@
 This is why both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible.
-Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [Nevalainen, Raumolin-Brunberg, and Mannila 2011 TODO].
-While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [Petré and Van de Velde 2018 TODO].
+Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [@nevalainen_diffusion_2011].
+While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [@petre_real-time_2018].
 There is also variation in the language-internal factors influencing language change.
-While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [Fonteyn and Nini 2020 TODO].
-Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [Fonteyn and Petré 2022 TODO].
-Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [Guy 2013; Zenner, Kristiansen, and Geeraerts 2016; Van den Stock et al.
-2024 TODO].
+While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [@fonteyn_individuality_2020].
+Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [@fonteyn_probability_2022].
+Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [@guy_cognitive_2013;@zenner_individual_2016;@van_den_stock_individual_2024].
 

### 2025-08-20 paper/paper.qmd
references added

@@
 Linguistically, the effects of networks have been studied before.
-Milroy and Milroy [1985 TODO], who base themselves on Granovetter [1973 TODO] and Rogers and Shoemaker [1971 TODO], demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change.
+@milroy_linguistic_1985, who base themselves on @granovetter_strength_1973 and @rogers_communication_1971, demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change.
 Strong ties (e.g.

### 2025-08-20 paper/paper.qmd
references + network theory

@@
 Once exposed to these new forms, individuals connected through weak ties may adopt them and, through their strong ties, introduce them to their close-knit circles.
+This dynamic does not affect all individuals equally: some are positioned to introduce innovations into the network, while others play a crucial role in amplifying and spreading them.
 
-- leaders / loaners
-- gedrag van centrale figuren
-- alle andere dingen die interessant zouden kunenn zijn
+Within the propagation of linguistic change, different roles can be distinguished.
+Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel linguistic features from outside their immediate community [@rogers_diffusion_2003].
+Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population.
+Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003].
+In this way, innovators and early adopters together bridge the gap between the periphery and the core of a community, ensuring that new linguistic forms do not remain isolated but instead gain broader social traction [@granovetter_strength_1973;@milroy_linguistic_1985].
+The idea that innovation originates in the periphery of a network before it can spread has been attested before in network studies [@van_de_leemput_transformation_2024], but not whithin linguistics.
 
-Except for small-scale studies [e.g.
-@labov_study_1968;@milroy_belfast_1978], it has been impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
+Except for some (often small-scale) studies [e.g.
+@labov_study_1968;@milroy_belfast_1978;@nevalainen_social_2015;@sharma_scalar_2017;@paradowski_how_2022] and simulations [@ke_language_2008;@ogura_dynamic_2008], it has been near impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
 Again, social media offer an opportunity here.

### 2025-08-20 paper/paper.qmd
pages added to references

@@
 Within the propagation of linguistic change, different roles can be distinguished.
-Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel linguistic features from outside their immediate community [@rogers_diffusion_2003].
+Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel linguistic features from outside their immediate community [@rogers_diffusion_2003: 282-283].
 Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population.
-Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003].
+Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003: 282-283].
 In this way, innovators and early adopters together bridge the gap between the periphery and the core of a community, ensuring that new linguistic forms do not remain isolated but instead gain broader social traction [@granovetter_strength_1973;@milroy_linguistic_1985].

### 2025-08-21 paper/paper.qmd
'how' added to sentence
typo removed: double a

@@
 This will prove especially useful for this study on individual variation, since we need several tweets in order to gauge the language use of a specific speaker.
-For each author, we also know many accounts they follow, and how many accounts they are followed by.
+For each author, we also know how many accounts they follow, and how many accounts they are followed by.
 This is a metric that is useful for our questions about network influences.
@@
 @tbl-other-coefficients gives an overview of the "control" coefficients that were included in order to have multifactorial control for the individual variation.
-Since the innovative *bent* variant was encoded as outcome "1", and the conservative *zijt* was encoded as outcome "0", positive coefficients mean a a correction towards the innovative variant, while negative corrections mean a correction towards the conservative variant.
+Since the innovative *bent* variant was encoded as outcome "1", and the conservative *zijt* was encoded as outcome "0", positive coefficients mean a correction towards the innovative variant, while negative corrections mean a correction towards the conservative variant.
 These corrections must be interpreted from the situation expressed in the intercept, a "reference situation" that is defined as follows:

### 2025-08-21 paper/paper.qmd
typo: slights -> slight
typo correction

@@
 We see that there is a bi-modal distribution in the variation coefficients.
-The first distribution shows many slights corrections towards the conservative form (first bump).
+The first distribution shows many slight corrections towards the conservative form (first bump).
 The second distribution shows a smaller number of larger corrections towards the innovative form (second bump).
@@
 One might wonder what the profile of these rare innovators is.
-Perhaps they they live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
+Perhaps they live close to the border in their specific dialect regions, and are therefore "atypically" innovative for their region.
 To answer this question, we built a Generalised Additive Model or GAM [@hastie_generalized_1987].

### 2025-08-21 paper/paper.qmd
typo fix

@@
 In our case, we want to know how the language users who are thought to be influential in our network behave.
-Are they are the forefront of innovation, or are they conservative?
+Are they at the forefront of innovation, or are they conservative?
 Depending on what profile we find, we might be able to discern in what phase of diffusion the *gij bent* innovation is situated.
@@
 To answer this question, we built a common linear regression model.
-We model the coefficients in term of the influence of the users, but we also supplement our analysis with the dialect and gender distinctions we discussed earlier.
+We model the coefficients in terms of the influence of the users, but we also supplement our analysis with the dialect and gender distinctions we discussed earlier.
 Bundling all these possible influences in the same model will ensure that we do not accidentally assign variation between language users to the wrong source.

### 2025-08-21 paper/paper.qmd
paragraph about network influence

@@
 This means that the more influential a speaker is in the Twitter network, the more likely they are to use the new, innovative *gij bent* form.
-[Todo Julie uitleg hoe en waarom dit zo is]
-
-[network effect explanation]
+In other words, the innovative *gij bent* form is not confined to peripheral innovators but is actively promoted by more central and prestigious figures in the Twitter network.
+This finding aligns with network-based theories of diffusion, in which highly connected early adopters play a crucial role in amplifying and legitimizing innovations [@rogers_diffusion_2003: 282-283].
+It also indicates that *gij bent* may have progressed beyond the initial stage of peripheral innovation, i.e.
+the stage in which the innovators are crucial, and entered a phase in which socially visible and influential users help to normalize the form.
 

### 2025-08-21 paper/paper.qmd
paragraph introducing terms innovators and early adopters

@@
 Within the propagation of linguistic change, different roles can be distinguished.
-Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel linguistic features from outside their immediate community [@rogers_diffusion_2003: 282-283].
+Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283].
 Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population.

### 2025-08-22 paper/paper.qmd
references + place in the S-curve

@@
 
-Within the propagation of linguistic change, different roles can be distinguished.
-Innovators, who are hypothesized to be less central and only loosely connected to others through weak ties, acquiring novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283].
-Early adopters, by contrast, are hypothesized to be more centrally positioned and to enjoy a higher degree of connectivity within the population.
+Within the propagation of innovations, different roles can be distinguished.
+Innovators, who are less central and only loosely connected to others through weak ties, acquiring novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283].
+Early adopters, by contrast, are more centrally positioned and enjoy a higher degree of connectivity within the population.
 Through their many strong ties, they amplify and legitimize the innovation, spreading it efficiently across their dense local networks [@rogers_diffusion_2003: 282-283].
@@
 
+The observed synchronic variation can also be interpreted through the framework of binary language change, where a new variant, *gij bent*, competes with an older one, *gij zijt*.
+Such binary changes are typically modeled using an S-curve [@speelman_logistic_2014], which plots the cumulative adoption of the innovation over time.
+This S-curve has a bell-shaped counterpart, which does not capture the cumulative adoption, but instead captures the rate of adoption at any given point in time: few individuals adopt at the very beginning, adoption peaks as the innovation gains momentum, and then levels off once most speakers have shifted.
+Diffusion research has shown that the individuals driving this process can be categorized into five adopter groups, defined mathematically by standard deviations around the mean adoption time [@rogers_diffusion_2003: PAGES]: innovators, early adopters, early majority, late majority, and laggards (see FIGURE BELOW).
+As already hinted at in @sec-introduction, each of these categories is embedded in the network in a different way.
+Innovators, positioned at the periphery and connected through weak ties, acquire innovations from outside their immediate community and initiate change.
+Early adopters, in contrast, are more centrally embedded and exert strong influence through their many strong ties, thereby accelerating diffusion and granting legitimacy to the innovation [REFS].
+Our finding that more influential Twitter users are more likely to employ *gij bent* suggests that this form has moved beyond the initial innovator stage and is now being amplified by early adopters.
+In this way, we can infer in which stage of the S-curve the change is situated: between the second and the first standard deviation before the mean.
+
+```{r adopter-categories}
+# Load libraries
+library(ggplot2)
+
+# Simulated time steps
+time <- seq(0, 20, 0.1)
+
+# Logistic S-curve (cumulative adoption)
+s_curve <- 100 / (1 + exp(-0.6 * (time - 10)))
+
+# Bell curve (adoption rate, derivative of logistic)
+bell_curve <- dnorm(time, mean = 10, sd = 2.5) * 100
+
+# Combine into dataframe
+df <- data.frame(time, s_curve, bell_curve)
+
+# Define cutoffs for adopter categories
+mean_time <- 10
+sd_time <- 2.5
+cuts <- data.frame(
+  x = c(mean_time - 2*sd_time, mean_time - sd_time, mean_time,
+        mean_time + sd_time, mean_time + 2*sd_time),
+  label = c("Innovators", "Early Adopters", "Early Majority", 
+            "Late Majority", "Laggards"),
+  col = c("red", "orange", "green3", "darkgreen", "blue")
+)
+
+# Plot
+ggplot(df, aes(x = time)) +
+  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), size = 1) +
+  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), size = 1, linetype = "dashed") +
+  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
+  scale_colour_manual(
+    name = "Legend",
+    values = c("S-curve (Cumulative Adoption)" = "purple",
+               "Bell Curve (Adoption Rate)" = "deeppink",
+               "Innovators" = "red",
+               "Early Adopters" = "orange",
+               "Early Majority" = "goldenrod3",
+               "Late Majority" = "darkgreen",
+               "Laggards" = "blue")
+  ) +
+  labs(
+    title = "S-curve and Bell Curve",
+    x = "Time step",
+    y = "Adoption percentage"
+  ) +
+  theme_minimal(base_size = 14)
+
+```
+
 ## Conclusion

### 2025-09-26 analysis/2-analysis-gam.R
Load rich coefficients for building the GAM

@@ -9,6 +9,7 @@ library(nngeo) # removing the Brussels hole
 
 source("0-common.R")
 
+coefficients <- read.csv("../output/gij_bent_coefficients_rich.csv")
 df_solo <- coefficients
 
 #

### 2025-09-28 paper/paper.qmd
Punctuation and text flow

@@
 Rather, it is widely accepted within this branch that language arises out of the many interactions that language users have with each other [@keller_language_1994].
-As such, language becomes a "complex-adaptive system" [@steels_language_2000;@beckner_language_2009;@ellis_what_2012;@kretzschmar_language_2015], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components, language users.
+As such, language becomes a "complex-adaptive system" [@steels_language_2000;@beckner_language_2009;@ellis_what_2012;@kretzschmar_language_2015], a system without a single authoritative control, constructed through the simple yet numerous interactions of its components: language users.
 While each speaker of a language (be it Dutch, English or Maori) has their own personalised representation of the rules and constraints that they think make up that language, these representations have enough in common in order to warrant talking about a shared "code", or more broadly, a language.
@@
 While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers.
-This is why both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible.
+This is why both from a usage-based and a cognitive-linguistic perspective, the individual should be the primary unit of linguistic analysis where possible.
 Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [@nevalainen_diffusion_2011].
@@
 Linguistically, the effects of networks have been studied before.
-@milroy_linguistic_1985, who base themselves on @granovetter_strength_1973 and @rogers_communication_1971, demonstrated that in a network both weak and strong ties are essential for the propagation of linguistic change.
+@milroy_linguistic_1985, who base themselves on @granovetter_strength_1973 and @rogers_communication_1971, demonstrated that in a network, both weak and strong ties are essential for the propagation of linguistic change.
 Strong ties (e.g.
@@
 acquaintances) form bridges between groups, facilitate the spread of linguistic innovations.
-Weak ties are especially crucial for exposing individuals to linguistic features or patterns that are not present within their immediate, tightly connected group, enabling the flow of new linguistic forms across disparate groups, broadening the reach of linguistic innovations.
+Weak ties are especially crucial for exposing individuals to linguistic features or patterns that are not present within their immediate, tightly connected group, enabling the flow of new linguistic forms across disparate groups and broadening the reach of linguistic innovations.
 Once exposed to these new forms, individuals connected through weak ties may adopt them and, through their strong ties, introduce them to their close-knit circles.
@@
 Within the propagation of innovations, different roles can be distinguished.
-Innovators, who are less central and only loosely connected to others through weak ties, acquiring novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283].
+Innovators, who are less central and only loosely connected to others through weak ties, acquire novel ideas from outside their immediate community [@rogers_diffusion_2003: 282-283].
 Early adopters, by contrast, are more centrally positioned and enjoy a higher degree of connectivity within the population.
@@
 Except for some (often small-scale) studies [e.g.
-@labov_study_1968;@milroy_belfast_1978;@nevalainen_social_2015;@sharma_scalar_2017;@paradowski_how_2022] and simulations [@ke_language_2008;@ogura_dynamic_2008], it has been near impossible to get an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
+@labov_study_1968;@milroy_belfast_1978;@nevalainen_social_2015;@sharma_scalar_2017;@paradowski_how_2022] and simulations [@ke_language_2008;@ogura_dynamic_2008;@fagyal_centers_2010], it has been near impossible to gain an elaborate insight into the social relationships of people on a large scale, let alone how these relationships relate to language.
 Again, social media offer an opportunity here.
@@
 In the largest part of the 20^th^ century, the language situation of Dutch in Flanders, the Dutch-speaking part of Belgium, could best be described as a *diglossia* [@auer_europe_2005].
-This means that the Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
+This means that Belgian Dutch was characterised by a dichotomy between standard language on the one hand, and dialects on the other hand.
 These two were the language modes available to speakers of Dutch.
-A large-scale language policy campaign at the timed attempted to teach those speakers who mastered only their local dialect the standard language.
+A large-scale language policy campaign at the time attempted to teach those speakers who mastered only their local dialect the standard language.
 While these efforts were well intended, the imposition of a "foreign" standard language -- the standard was imported from the Netherlands -- were met with limited enthusiasm by language users in Flanders.
@@
 To estimate the individual variation among our tweet authors, we would ideally have a quantitative measure which indicates the deviation of each user from the expected linguistic behaviour.
-Authors who do not deviate would be assigned a (near-)zero value, while those who *do* deviate would receive either a positive or negative value, depending on whether they exceed the expectations for their profiles, or actually go against it.
+Authors who do not deviate would be assigned a (near-)zero value, while those who *do* deviate would receive either a positive or negative value, depending on whether they exceed the expectations for their profiles, or go against it.
 In this way, our measure of individual variation truly expresses the peculiarities of each individual speaker.
@@
 The second metric, "Following", states how many other people's posts a user wants to see in their social media feed.
-Users who follow a large number of other users have the opportunity of being exposed to a larger linguistic pallette -- though this need not necessarily be the case.
+Users who follow a large number of other users have the opportunity of being exposed to a larger linguistic pallette, though this need not necessarily be the case.
 
@@
 
-To answer this question, we built a common linear regression model.
+To answer this question, we built a linear regression model.
 We model the coefficients in terms of the influence of the users, but we also supplement our analysis with the dialect and gender distinctions we discussed earlier.
@@
 This means that the more influential a speaker is in the Twitter network, the more likely they are to use the new, innovative *gij bent* form.
-In other words, the innovative *gij bent* form is not confined to peripheral innovators but is actively promoted by more central and prestigious figures in the Twitter network.
-This finding aligns with network-based theories of diffusion, in which highly connected early adopters play a crucial role in amplifying and legitimizing innovations [@rogers_diffusion_2003: 282-283].
+In other words: the innovative *gij bent* form is not confined to peripheral innovators, but is actively promoted by more central and prestigious figures in the Twitter network.
+This finding aligns with network-based theories of diffusion, in which highly connected early adopters play a crucial role in amplifying and legitimising innovations [@rogers_diffusion_2003: 282-283].
 It also indicates that *gij bent* may have progressed beyond the initial stage of peripheral innovation, i.e.
-the stage in which the innovators are crucial, and entered a phase in which socially visible and influential users help to normalize the form.
+the stage in which the innovators are crucial, entering a phase in which socially visible and influential users help to normalize the form.
 
@@
 This S-curve has a bell-shaped counterpart, which does not capture the cumulative adoption, but instead captures the rate of adoption at any given point in time: few individuals adopt at the very beginning, adoption peaks as the innovation gains momentum, and then levels off once most speakers have shifted.
-Diffusion research has shown that the individuals driving this process can be categorized into five adopter groups, defined mathematically by standard deviations around the mean adoption time [@rogers_diffusion_2003: PAGES]: innovators, early adopters, early majority, late majority, and laggards (see FIGURE BELOW).
+
+Diffusion research has shown that the individuals driving the diffusion process can be categorized into five adopter groups, defined mathematically by standard deviations around the mean adoption time [@rogers_diffusion_2003: PAGES]: innovators, early adopters, early majority, late majority, and laggards (see FIGURE BELOW).
 As already hinted at in @sec-introduction, each of these categories is embedded in the network in a different way.
@@
 
-## Conclusion
+## Discussion and conclusion
 

### 2025-09-28 paper/paper.qmd
Elastic net paper is out now

@@
 with mixed models).
-For additional details on elastic net regression for linguistics, see @sevenants_elastic_to_appear.
+For additional details on elastic net regression for linguistics, see @sevenants_investigating_2024.
 
@@
 
-Our influence metric is based on the priming ratio from @sevenants_elastic_to_appear and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013].
+Our influence metric is based on the priming ratio from @sevenants_investigating_2024 and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013].
 The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts.

### 2025-09-28 paper/paper.qmd
Add internal gij zijt/gij bent distribution in the data section

@@
 After all filtering operations, we were left with `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` unique authors.
+`r zijt_bent_table %>% .[["zijt"]] %>% formatn` tweets are attestations of conservative *zijt*, `r zijt_bent_table %>% .[["bent"]] %>% formatn` tweets are attestations of innovative *bent*.
+*Gij bent* usage is around `r bent_ratio %>% formatp` across language users.
+Note, however, that this is a global across-user metric, without any account for region- or gender-specific influences.
 

### 2025-09-28 analysis/0-common.R
Count 'gij bent' usage ratio across users

@@ -50,6 +50,17 @@ df <- subset(df, user_id %in%
 
 num_tweets_filtered <- dim(df)[1]
 num_users_filtered <- length(unique(df$user_id))
+zijt_bent_table <- df %>% xtabs(~ construction_type, .)
+per_user_ratios <- df %>%
+  group_by(user_id) %>%
+  summarize(
+    bent_count = sum(construction_type == "bent", na.rm = TRUE),
+    zijt_count = sum(construction_type == "zijt", na.rm = TRUE),
+    ratio = bent_count / (bent_count + zijt_count)
+  )
+# Mean innovativeness ratio across uers
+bent_ratio <- mean(per_user_ratios$ratio, na.rm = TRUE)
+
 
 # Only one tweet per user
 one_user_one_tweet <- function(df) {

### 2025-09-28 analysis/0-common.R
Remove unknown gender from user count computation

@@ -49,7 +49,7 @@ df <- subset(df, user_id %in%
               names(user_id_counts[user_id_counts >= MIN_TWEET_THRESHOLD]))
 
 num_tweets_filtered <- dim(df)[1]
-num_users_filtered <- length(unique(df$user_id))
+num_users_filtered <- length(unique(df %>% no_unknown_gender %>% .$user_id))
 zijt_bent_table <- df %>% xtabs(~ construction_type, .)
 per_user_ratios <- df %>%
   group_by(user_id) %>%

### 2025-09-28 analysis/0-common.R
Move constants to be used in the paper down in the common R script

@@ -48,19 +48,6 @@ user_id_counts <- table(df$user_id)
 df <- subset(df, user_id %in%
               names(user_id_counts[user_id_counts >= MIN_TWEET_THRESHOLD]))
 
-num_tweets_filtered <- dim(df)[1]
-num_users_filtered <- length(unique(df %>% no_unknown_gender %>% .$user_id))
-zijt_bent_table <- df %>% xtabs(~ construction_type, .)
-per_user_ratios <- df %>%
-  group_by(user_id) %>%
-  summarize(
-    bent_count = sum(construction_type == "bent", na.rm = TRUE),
-    zijt_count = sum(construction_type == "zijt", na.rm = TRUE),
-    ratio = bent_count / (bent_count + zijt_count)
-  )
-# Mean innovativeness ratio across uers
-bent_ratio <- mean(per_user_ratios$ratio, na.rm = TRUE)
-
 
 # Only one tweet per user
 one_user_one_tweet <- function(df) {
@@ -74,3 +61,17 @@ no_unknown_gender <- function(df) {
   return(df)
 }
 
+# Constants to be used in the paper
+
+num_tweets_filtered <- dim(df)[1]
+num_users_filtered <- length(unique(df %>% no_unknown_gender %>% .$user_id))
+zijt_bent_table <- df %>% xtabs(~ construction_type, .)
+per_user_ratios <- df %>%
+  group_by(user_id) %>%
+  summarize(
+    bent_count = sum(construction_type == "bent", na.rm = TRUE),
+    zijt_count = sum(construction_type == "zijt", na.rm = TRUE),
+    ratio = bent_count / (bent_count + zijt_count)
+  )
+# Mean innovativeness ratio across uers
+bent_ratio <- mean(per_user_ratios$ratio, na.rm = TRUE)

### 2025-09-28 paper/paper.qmd
Fix small typo
Add overview of eliminated and non-eliminated coefficients

@@
 
-First, we will look at the coefficient globally.
+Of the `r num_users_filtered %>% formatn` unique tweet authors in our dataset, our elastic net regression was able to estimate `r coefficients %>% filter(coefficient != 0) %>% dim %>% .[1] %>% formatn` innovation patterns.
+This means that `r coefficients %>% filter(coefficient == 0) %>% dim %>% .[1] %>% formatn` authors either did not meaningfully deviate in their *gij bent* or *gij zijt* usage from what is expected from them.
+It could also be that the model did not have enough data to reliably estimate an innovativeness score, but since we imposed a lower limit of 10 attestations per user, this should generally not be the case.
+
 The density plot of the variation coefficients in @fig-general-density gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc..

### 2025-09-28 paper/paper.qmd
Add coefficients overview plots

--- 2025-09-28 paper/paper.qmd
@@
 
-First, we will look at the coefficient globally.
-The density plot of the variation coefficients in @fig-general-density gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc..
+```{r coefficients-computation}
+#| output: false
+
+coefficients$removed <- ifelse(coefficients$coefficient == 0, TRUE, FALSE)
+removed_distribution <- xtabs(~ removed, data=coefficients)
+removed_distribution_prop <- removed_distribution %>% prop.table()
+
+coefficients_non_zero <- coefficients[coefficients$removed == FALSE,]
+coefficients_non_zero$innovativeness <- ifelse(coefficients_non_zero$coefficient > 0, "innovative", "conservative")
+non_zero_distribution <- xtabs(~ innovativeness, data=coefficients_non_zero)
+non_zero_distribution_prop <- non_zero_distribution %>% prop.table()
+
+non_eliminated_count <- removed_distribution[["FALSE"]]
+eliminated_count <- removed_distribution[["TRUE"]]
+
+innovative_count <- non_zero_distribution[["innovative"]]
+conservative_count <- non_zero_distribution[["conservative"]]
+```
+
+Of the `r num_users_filtered %>% formatn` unique tweet authors in our dataset, our elastic net regression model was able to estimate `r non_eliminated_count %>% formatn` innovation patterns (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors).
+This means that `r eliminated_count %>% formatn` authors (`r removed_distribution_prop[["TRUE"]] %>% formatp` of all authors) did not meaningfully deviate in their *gij bent* or *gij zijt* usage from what is expected from them.
+It could also be that the model did not have enough data to reliably estimate an innovativeness score, but since we imposed a lower limit of 10 attestations per user, this should generally not be the case.
+Of the `r non_eliminated_count %>% formatn` innovativeness profiles, `r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) are innovative (correction towards innovative *bent*), while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) are conservative (correction towards conservative *zijt*).
+An overview is given in @fig-coefficient-plots-1 and @fig-coefficient-plots-2.
+
+```{r}
+#| label: fig-coefficient-plots
+#| column: screen-inset-shaded
+#| layout-ncol: 3 
+#| fig-subcap:
+#|   - "Proportion of removed and retained coefficients"
+#|   - "Proportion of innovative and conservative author profiles" 
+#|   - "A density plot describing the individual variation coefficients in our dataset.
+The left side of the plot (negative coefficients) shows corrections towards the conservative form, the right side of the plot (positive coefficients) shows corrections towards the innovative form."
+options(scipen=999)
+
+# Retained-removed distribution
+row.names(removed_distribution) <- c("retained", "removed")
+barplot(removed_distribution %>% sort(decreasing=TRUE),
+        ylim=range(pretty(c(0, removed_distribution))))
+
+# Innovative-conservative distribution
+barplot(non_zero_distribution %>% sort(decreasing=TRUE),
+        ylim=range(pretty(c(0, non_zero_distribution))))
+
+coefficients %>%
+  ggplot(aes(x = coefficient)) +
+  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.5) +
+  geom_vline(xintercept=0, color="black", linewidth=1, linetype="dotdash")
+```
+
+The density plot of the variation coefficients in @fig-coefficient-plots-3 gives a global overview of the how each language user "deviates" from what is expected given their gender, location etc..
 Negative coefficients on the left side of the plot show deviations of individual language users towards the conservative *gij zijt*.
@@
 We will attempt to tease out this distinction in the next section.
-
-```{r #fig-general-density}
-#| fig-cap: A density plot describing the individual variation coefficients in our dataset.
-The left side of the plot (negative coefficients) shows corrections towards the conservative form, the right side of the plot (positive coefficients) shows corrections towards the innovative form.
-coefficients %>%
-  ggplot(aes(x = coefficient)) +
-  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.5) +
-  geom_vline(xintercept=0, color="black", linewidth=1, linetype="dotdash")
-```
 
@@
 In these dialects, the values gravitate towards more conservative corrections.
-With these results, we have an explanation for the bi-modal nature of @fig-general-density: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region, and therefore correct "downwards".
+With these results, we have an explanation for the bi-modal nature of @fig-coefficient-plots-3: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region, and therefore correct "downwards".
 The second distribution, centred *above* zero, consists mostly of eager innovators from the already innovative Brabant dialect area.

### 2025-09-28 paper/paper.qmd
Add Pareto reference

@@
 users who have more followers than they themselves follow people.
-This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006].
+This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006; related to the Pareto Principle: @juran_non_1975].
 Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.

### 2025-09-28 paper/paper.qmd
Add caption to boxplot figure

@@
 Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.
+@fig-influence-boxplot shows the distribution of the influence metric.
 
 ```{r #fig-influence}
+#| label: fig-influence-boxplot
+#| caption: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.
+
 boxplot(coefficients$influence, horizontal = T)

### 2025-09-28 paper/paper.qmd
Stylise emmeans
Explain behaviour reversal better

@@
 Therefore, the differences which we discussed in @sec-group-variation are not different enough to the degree that they are actually distinct.
-Still, the fact that the *tendency* is clearly there is still interesting, and the reversal of the extreme values of course still holds.
+Still, the fact that the *tendency* is clearly there is still interesting, and the idea that individual behaviour can be the reverse of a general trend of course still holds.
 
@@
 In addition, we wanted to know whether there are also differences *between* the non-Brabant dialact areas.
-To investigate this, we ran a post-hoc analysis through emmeans [@emmeans].
+To investigate this, we ran a post-hoc analysis through `emmeans` [@emmeans].
 In this post-hoc analysis, we check for each dialect area pair whether there are significant differences in individual variation between the two.

### 2025-09-28 paper/paper.qmd
Change deprecated properties in Julies' graph

@@
 ```{r adopter-categories}
+#| echo: FALSE
+
 # Load libraries
@@
 ggplot(df, aes(x = time)) +
-  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), size = 1) +
-  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), size = 1, linetype = "dashed") +
+  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
+  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
   geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +

### 2025-09-28 paper/paper.qmd
Rename influence boxplot again
Remove uppercase in Julie graph title

@@
 The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`).
-The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e.
+The boxplot in @fig-influence-boxplot shows that our dataset generally consists of more influential figures, i.e.
 users who have more followers than they themselves follow people.
@@
 Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.
-@fig-influence-boxplot shows the distribution of the influence metric.
 
@@
   labs(
-    title = "S-curve and Bell Curve",
+    title = "S-curve and bell curve",
     x = "Time step",

### 2025-09-28 paper/paper.qmd
Remove uppercase in Julie graph legend

@@
     name = "Legend",
-    values = c("S-curve (Cumulative Adoption)" = "purple",
-               "Bell Curve (Adoption Rate)" = "deeppink",
+    values = c("S-curve (cumulative adoption)" = "purple",
+               "Bell curve (adoption Rate)" = "deeppink",
                "Innovators" = "red",
-               "Early Adopters" = "orange",
-               "Early Majority" = "goldenrod3",
-               "Late Majority" = "darkgreen",
+               "Early adopters" = "orange",
+               "Early majority" = "goldenrod3",
+               "Late majority" = "darkgreen",
                "Laggards" = "blue")

### 2025-09-28 paper/paper.qmd
I had broken the legend colours

@@
 
+# TODO volgorde legende is fucked
+
 # Load libraries
@@
         mean_time + sd_time, mean_time + 2*sd_time),
-  label = c("Innovators", "Early Adopters", "Early Majority", 
-            "Late Majority", "Laggards"),
+  label = c("Innovators", "Early adopters", "Early majority", 
+            "Late majority", "Laggards"),
   col = c("red", "orange", "green3", "darkgreen", "blue")
@@
 ggplot(df, aes(x = time)) +
-  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
-  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
+  geom_line(aes(y = s_curve, colour = "S-curve (cumulative adoption)"), linewidth = 1) +
+  geom_line(aes(y = bell_curve, colour = "Bell Curve (adoption rate)"), linewidth = 1, linetype = "dashed") +
   geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +

### 2025-09-30 paper/paper.qmd
Finish conclusion, more or less

@@
 By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region.
-Through elastic net regression, a modern regression technique, deviations were found for TODO users in the dataset (TODO percent).
-TODO more conservative, TODO more innovative We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects.
-The Brabant region deviates towards the innovative form, the other regions deviate towards the conservative form.
+Through elastic net regression, a modern regression technique, deviations were found for `r non_eliminated_count %>% formatn` users in the dataset (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors).
+`r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were innovative, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were conservative.
+We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects.
+The Brabant region correct towards the innovative form, the other regions correct towards the conservative form.
 We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.
@@
 Our results show that the socially influential users in our dataset are generally more innovative.
-This might indicate that the diffusion of the innovative *bent* variant is in the TODO phase.
+This might indicate that the diffusion of the innovative *bent* variant might be currently in the "early adopters" stage.
+The innovative variant can therefore be assumed to diffuse more broadly in the future.
+Of course, it remains to be seen just how accurate the network measure is for accurately predicting the current stage in the diffusion of an innovation.
+A diachronic network study of a fully completed diffusion pattern could shed more light in this regard.
+
+Finally, our study shows that CBD is still very much "in flux".
+While one cannot speak of a single, monolithic CBD variety, the geospatial findings suggest that a horizontal expansion of at least this Antwerp-Brabantian feature could be possible.
+This would go against previous findings arguing against the "Brabant expansion", but it is not unthinkable when one takes the perspective of individual variation.
+As was mentioned in @sec-introduction, individual linguistic behaviour is not uniformly progressive or conservative.
+An uneven diffusion of CBD features might find its roots in this non-uniform individual behaviour.
 

### 2025-09-30 paper/paper.qmd
Finish conclusion

@@
 
-## Discussion and conclusion
+## Discussion
 
-This article aimed to investigate whether and how speakers deviate from general expectations.
-We focussed on the affordances these deviations, defined as individual variation, can bring for alternation research, as well as what implicit network structures can teach us about the spread of linguistic innovations.
-We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors.
-By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region.
+This article aimed to investigate the role of individual variation and network effects in language change through a study of an ongoing innovation in Colloquial Belgian Dutch (CBD).
+In this section, we will discuss to what extent we were able to associate linguistic behaviour to specific individuals and their place within a larger community.
+
+First, we wanted to investigate to what extent individuals differ in their linguistic behaviour from the "general" behaviour predicted from their dialect area and gender.
+We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch (CBD) with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors.
+By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on the aforementioned general factors like gender and dialect region.
 Through elastic net regression, a modern regression technique, deviations were found for `r non_eliminated_count %>% formatn` users in the dataset (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors).
-`r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were innovative, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were conservative.
+`r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were more innovative than expected from their profile, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were more conservative than expected.
 We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects.
@@
 The consequences of our findings are twofold.
-In a broad sense, our results show that individual variation exists, and in fact is abundant in our case.
+In general, our results show that individual variation exists, and in fact is abundant in our case.
 This illustrates that an important dimension of variation is likely lost in traditional regression models.
-The regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random.
+On a more specific level, the regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random.
 In a sense, it means that there is "second order variation", variation *within* the variation, so to say.
@@
 
-The predictive nature of the geospatial distributions bring us to the network analysis of our study.
+The predictive nature of the geospatial distributions bring us to the network component of our study.
 Our results show that the socially influential users in our dataset are generally more innovative.
@@
 A diachronic network study of a fully completed diffusion pattern could shed more light in this regard.
+Still, it seems that network or other influence information about speakers could function as a "derivative function" in the S-curve, indicating what direction the innovation is heading.
 
-Finally, our study shows that CBD is still very much "in flux".
+Finally, our study shows that CBD as a variety is still very much "in flux".
 While one cannot speak of a single, monolithic CBD variety, the geospatial findings suggest that a horizontal expansion of at least this Antwerp-Brabantian feature could be possible.
@@
 An uneven diffusion of CBD features might find its roots in this non-uniform individual behaviour.
-
-- [algemeen idee van de individuele variatie]
-- [conclusies voor tussentaal]
-- [idee dat je op deze manier ook kunt vaststellen in welke fase van de verspreiding een fenomeen zit]
+This shows that a focus on the individual, as well as the place of that individual within the larger community, could offer new perspectives on existing questions in studies of language change.

### 2025-09-30 paper/paper.qmd
Add abstract

@@
 abstract: |
-  TODO
+  Language change finds its origins in individual variation.
+Individual behaviour, however, is rarely taken into account in variationist studies.
+In this study, we look at innovative *gij bent* from Colloquial Belgian Dutch through a corpus of 16,968 tweets by 555 authors.
+With elastic net regression, we build a linguistic profile for each individual author: 51% of authors are more innovative than one would expect from their dialect area and gender, 49% are more conservative.
+When we plot these deviations regionally, we see a potential future horizontal diffusion pattern.
+Additionally, we find that influential tweet authors tend to be more innovative.
+Therefore, *gij bent* might currently be in the "early adopters" stage of diffusion.
+In general, our results show that a focus on the individual offers new perspectives which might remain hidden in traditional variationist analyses.
 execute:

### 2025-10-01 paper/paper.qmd
Make sure caption appears for influence figure
Voeg TODO toe aan conclusie

@@
 #| label: fig-influence-boxplot
-#| caption: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.
+#| fig-cap: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.
 
@@
 This shows that a focus on the individual, as well as the place of that individual within the larger community, could offer new perspectives on existing questions in studies of language change.
+
+[[ de discussie mag best wat uitgebreider - nu wat te summier ]]

### 2025-10-01 paper/paper.qmd
Better integrate Julie's part into the main text

@@
 Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds.
-We see this, for example, in probabilistic grammar, the branch of variation studies that investigates how variation reflects competing constraints on linguistic choices [@grafmiller_general_2018].
-Still, on a theoretical level, it is regrettable that models of variation do not start from the lowest common denominator of this variation: the language user.
 
@@
 
+Still, this does not mean that language users necessarily all behave in the same way.
+@nevalainen_diffusion_2011 show that linguistic behaviour is not uniformly progressive or conservative, either within individuals or among groups.
+While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [@petre_real-time_2018].
+There is also variation in the language-internal factors influencing language change.
+While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [@fonteyn_individuality_2020].
+Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [@fonteyn_probability_2022].
+Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [@guy_cognitive_2013;@zenner_individual_2016;@van_den_stock_individual_2024].
+
+Most studies concerning individual variation involve an analysis of historical data, or are based on smaller-scale surveys [e.g.
+@labov_study_1968;@milroy_belfast_1978].
 Contrastively, the advent of social media offers a unique opportunity for variationist research.
-Social media platforms offer an insight into the language systems of a large number of people.
-Whereas previously it was possible to gauge the linguistic profile of only a small group of people [e.g.
-@labov_study_1968;@milroy_belfast_1978], social media offer linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [@vandekerckhove_perception_2007, 255].
+Social media platforms offer an insight into the language systems of a large number of people, offering linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [@vandekerckhove_perception_2007, 255].
 In addition, social media data of course do not provide access to *all* of language for *all* users of a language system; not all utterances are made on social media, nor are all language users active on social media platforms.
@@
 
-1. What affordances does a focus on individual variation bring us in the context of alternation research, especially in contrast to traditional, aggregated alternation research?
+1. What affordances does a focus on individual variation bring us in the context of contemporary alternation research, especially in contrast to traditional, aggregated alternation research?
 
@@
 This is why both from a usage-based and a cognitive-linguistic perspective, the individual should be the primary unit of linguistic analysis where possible.
-Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [@nevalainen_diffusion_2011].
-While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [@petre_real-time_2018].
-There is also variation in the language-internal factors influencing language change.
-While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [@fonteyn_individuality_2020].
-Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [@fonteyn_probability_2022].
-Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [@guy_cognitive_2013;@zenner_individual_2016;@van_den_stock_individual_2024].
 

### 2025-10-01 paper/paper.qmd
Remove part of Julie's input

@@
 The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.
-
-It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals.
-While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers.
-This is why both from a usage-based and a cognitive-linguistic perspective, the individual should be the primary unit of linguistic analysis where possible.
 

### 2025-10-01 paper/paper.qmd
More introduction rewriting

@@
 
-Linguistically, the effects of networks have been studied before.
+Linguistically, the effects of such networks have been studied before.
 @milroy_linguistic_1985, who base themselves on @granovetter_strength_1973 and @rogers_communication_1971, demonstrated that in a network, both weak and strong ties are essential for the propagation of linguistic change.
@@
 In this way, innovators and early adopters together bridge the gap between the periphery and the core of a community, ensuring that new linguistic forms do not remain isolated but instead gain broader social traction [@granovetter_strength_1973;@milroy_linguistic_1985].
-The idea that innovation originates in the periphery of a network before it can spread has been attested before in network studies [@van_de_leemput_transformation_2024], but not whithin linguistics.
+The idea that innovation originates in the periphery of a network before it can spread has been attested before in network studies [@van_de_leemput_transformation_2024], but not within linguistics.
 
@@
 Then, we will introduce the dataset and describe how we modelled the linguistic profiles of the individual users with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study.
-Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.
+Next, we will show the results of our analyses, and discuss what implications they have for usage-based alternation research in general.
 

### 2025-10-01 paper/paper.qmd
Fix: suited to determining > suited FOR determining

@@
 To answer the two research questions stated above, we follow up on a study by Sevenants [@sevenants_zijt_2024] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD).
-To compute the individual variation of different language users, we will use elastic net regression, a technique suited to determining individual variation.
+To compute the individual variation of different language users, we will use elastic net regression, a technique suited for determining individual variation.
 First, we will introduce the *gij bent* CBD linguistic innovation.

### 2025-10-01 paper/paper.qmd
Rework elastic net section

@@
 We can use this behaviour to enter many predictors in the same analysis at once, and let the model decide which ones are actually interesting.
+In our case, we can estimate a correction term for each speaker separately, and have the elastic net regression model figure out which speakers deviate from expectations and which do not.
+The latter speakers will then be eliminated from the model.
 
@@
 with mixed models).
+
+Finally, note that regularised regression can be realised in two different ways: through ridge regression, or through lasso regression.
+In ridge regression, regularisation only brings coefficients asymptotically close to zero, whereas in lasso regression, coefficients can be zeroed out entirely.
+Elastic net offers a combination of both through a parameter called "alpha".
+A zero value for alpha means only ridge regression is used, the opposite leads to only lasso regression.
+A combination of both techniques can be beneficial depending on the dataset.
 For additional details on elastic net regression for linguistics, see @sevenants_investigating_2024.
 
-In general, then, elastic net regression lends itself nicely to research into individual variation.
+In general, elastic net regression lends itself well to research into individual variation.
 With elastic net, we modelled the presence of either *zijt* (conservative) or *bent* (innovative) as a logistic response variable.
@@
 For our analysis, we used ElasticToolsR [@sevenants_elastic_2024], a package for the R language [@r_language_2021] which simplifies running elastic net regression models.
+This package also automatically determines the best split between ridge and lasso regression.
 

### 2025-10-01 paper/paper.qmd
Rewrite conclusion

@@
 `r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were more innovative than expected from their profile, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were more conservative than expected.
-We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects.
-The Brabant region correct towards the innovative form, the other regions correct towards the conservative form.
+We analysed these deviations regionally, and found that the innovative corrections were mostly associated with the central Brabant region, while the conservative corrections were mostly associated with the other Flemish dialect regions.
 We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.
 
-The consequences of our findings are twofold.
-In general, our results show that individual variation exists, and in fact is abundant in our case.
-This illustrates that an important dimension of variation is likely lost in traditional regression models.
-On a more specific level, the regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random.
-In a sense, it means that there is "second order variation", variation *within* the variation, so to say.
+In general, these results show that individual variation exists, and in fact is abundant in our case.
+This illustrates that an important dimension of variation is likely lost in traditional regression models (i.e.
+the bi-modal distribution seen in @fig-coefficient-plots-1).
+In addition, we see that individual variation is also not random.
+When we look at the individual corrections geographically, we find innovative types near dialect borders, while conservative types are more isolated.
+In a sense, this means that there is "second order variation", variation *within* the variation, so to say.
 The geospatial distribution also provides an opportunity to anticipate upcoming diffusion patterns.
@@
 This shows that a focus on the individual, as well as the place of that individual within the larger community, could offer new perspectives on existing questions in studies of language change.
-
-[[ de discussie mag best wat uitgebreider - nu wat te summier ]]

### 2025-10-01 paper/paper.qmd
Finish Julie figure

@@
 #| echo: FALSE
+#| fig-cap: S-curve showing the cumulative adoption or diffusion of an innovation.
+The bell curve is its derivative and shows the adoption rate over time.
+For *gij bent*, we are assumed to currently be in the "Early adopters" phase.
 
-# TODO volgorde legende is fucked
-
-# Load libraries
-library(ggplot2)
-
-# Simulated time steps
+# Rescale time to 0–100
 time <- seq(0, 20, 0.1)
+time_rescaled <- time * 5   # 0–100
 
@@
 
-# Combine into dataframe
-df <- data.frame(time, s_curve, bell_curve)
+# Combine into dataframe with rescaled x
+df <- data.frame(time = time_rescaled, s_curve, bell_curve)
 
-# Define cutoffs for adopter categories
-mean_time <- 10
-sd_time <- 2.5
-cuts <- data.frame(
-  x = c(mean_time - 2*sd_time, mean_time - sd_time, mean_time,
-        mean_time + sd_time, mean_time + 2*sd_time),
+# Build cutoff bands instead of single lines
+bands <- data.frame(
+  xmin = c(0, 
+           2.5, 
+           16, 
+           50, 
+           84),
+  xmax = c(2.5, 
+           16, 
+           50, 
+           84, 
+           100),
   label = c("Innovators", "Early adopters", "Early majority", 
             "Late majority", "Laggards"),
-  col = c("red", "orange", "green3", "darkgreen", "blue")
+  fill = c("red", "orange", "yellow", "darkgreen", "blue")
 )
 
-# Plot
+# Ensure correct order
+bands$label <- factor(
+  bands$label,
+  levels = c("Innovators", "Early adopters", "Early majority", "Late majority", "Laggards")
+)
+
+# Plot with bands
 ggplot(df, aes(x = time)) +
+  # bands (slightly transparent so curves still visible)
+  geom_rect(data = bands, aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf, fill = label),
+            alpha = 0.1, inherit.aes = FALSE) +
+
   geom_line(aes(y = s_curve, colour = "S-curve (cumulative adoption)"), linewidth = 1) +
-  geom_line(aes(y = bell_curve, colour = "Bell Curve (adoption rate)"), linewidth = 1, linetype = "dashed") +
-  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
-  scale_colour_manual(
-    name = "Legend",
-    values = c("S-curve (cumulative adoption)" = "purple",
-               "Bell curve (adoption Rate)" = "deeppink",
-               "Innovators" = "red",
+  geom_line(aes(y = bell_curve, colour = "Bell curve (adoption rate)"), linewidth = 1, linetype = "dashed") +
+  # label
+  annotate("text", x = 9.25, y = 52, label = "Now",
+           colour = "#7f6c4c", hjust = 0.5) +
+  scale_fill_manual(
+    name = "Adopter categories",
+    values = c("Innovators" = "red",
                "Early adopters" = "orange",
-               "Early majority" = "goldenrod3",
+               "Early majority" = "yellow",
                "Late majority" = "darkgreen",
@@
   ) +
+  scale_colour_manual(
+  name = "",
+  values = c("S-curve (cumulative adoption)" = "purple",
+             "Bell curve (adoption rate)" = "deeppink"),
+  limits = c("S-curve (cumulative adoption)",
+             "Bell curve (adoption rate)")) +  # enforce order
   labs(
-    title = "S-curve and bell curve",
-    x = "Time step",
-    y = "Adoption percentage"
+    x = "Time",
+    y = "Adoption"
   ) +
-  theme_minimal(base_size = 14)
-
+  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
+  theme_minimal(base_size = 14) +
+  theme(
+    legend.position = "bottom",
+    legend.box = "vertical"
+  ) +
+  guides(
+    colour = guide_legend(nrow = 1),  # lines legend
+    fill   = guide_legend(nrow = 2)   # bands legend
+  )
 ```
